---
title: "Lego Assembly Thesis Analysis"
author: "Amy Rae Fox & Zoe Kothari"
date: "2026-05-06"
output:
  html_document:
    theme: cosmo
    code_folding: hide
    fig_caption: yes
    number_sections: no
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    toc_depth: 6
  pdf_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
font-family: DejaVu Sans
mainfont: DejaVu Sans
editor_options: 
  markdown: 
    wrap: 72
---
## OPEN QUESTIONS

### STEP COMPLEXITY
- X complexity score import 
- X complexity score join to step duration
- todo something with step repeats / frequency 

### BY PARTICIPANT
- by participant experience
- by corsi 
- participant strategy 
mean step 0 time 
step 0 team 

### ERROR-PAIRS
- time——accuracy -- import error pairs 
- Do ppl who have fewer step repeats have more errors? (visualization
    of ERRORS X STEP frequency by person)
### STEP-PAIRS 
- strategy X errors

### SPEED/ACCURACY













## SETUP

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) #all the things
library(dplyr) #all the things 
library(lubridate) #timey-wimey
library(ggformula) #regression syntax viz
library(Hmisc) # %nin% operator
library(svglite) #saving ggplots as svgs
library(kableExtra) #table formatting
library(tidyr) #tidy data wrangling

## modelling
library(afex) #anova
library(lme4) #regression models
library(lmerTest) #regression models
library(sjPlot) #model plots
library(ggdist) #distributional viz
library(performance) #easyStats compare models
library(report) # ez reporting
library(insight) #ez model info 
library(glmmTMB) #negative binomial glm model 
library(broom.mixed) #tidy model tables mixed effects
library(ggstatsplot) ## plotting w/ statistical tests
```

### import lookup tables
```{r import-lookups}

## IMPORT STEP COMPLEXITY
lookup_step <- read_csv("data/input/lookup_step_complexity.csv", col_select = c('Step','complexity_score', 'complexity_category','Step_Code')) %>% 
  mutate(
    STEP = as_factor(Step),
    STEP_CODE = as_factor(Step_Code),
    COMPLEXITY = as_factor(complexity_category)
  ) %>% select(-Step,-Step_Code, -complexity_category)

## IMPORT ERROR CODES
lookup_errors <- read_csv("data/input/lookup_errors.csv") %>% 
  mutate(across(where(is.character), as.factor))

```


### import steps
```{r import-steps}

## DF_STEPS_RAW
## maxQDA export of all retrieved segments for the query (all documents) + (highest level step code [includes each numbered step + Step Repeat + Flipping/Tapping Through Fast])
## NOTE: need to handle Step Repeat + Flipping/Tapping Through Fast seperately 
df_steps_raw <- read_csv("data/input/wip_steps.csv", col_select = 
                       c(`Document name`,
                         `Code`,
                        `Beginning`,
                        `End`
                         ),
                     show_col_types=FALSE) %>% 
    rename(
      START =  `Beginning`,
      END = `End`
    ) %>%
    separate('Document name', into = c("PID", "JAR","FORMAT"), sep = "_") %>% 
    separate('Code', into = c("MASTER_STEP", "STEP"), sep = '>') %>% 
    ## strip weird end stuff from times
    separate(END, into = c("END", "JUNK"), sep = ',') %>% 
    separate(START, into = c("START", "JUNK"), sep = ',') %>% 
  mutate(
    PID = as_factor(PID),
    JAR = as_factor(JAR),
    FORMAT = as_factor(FORMAT),
    # ERROR_GROUP = as_factor(str_trim(ERROR_GROUP)),
    STEP = as_factor(str_trim(STEP)),
    # MASTER_STEP = as_factor(MASTER_STEP),
    START = hms::as_hms(START),
    END = hms::as_hms(END),
    DURATION = END-START
  ) |> 
## CREATE ORDER FACTOR 
  mutate(
    ORDER = case_when(
      (JAR == "jar1" & FORMAT == "B") |
      (JAR == "jar2" & FORMAT == "A") ~ "BOOK_FIRST",

      (JAR == "jar1" & FORMAT == "A") |
      (JAR == "jar2" & FORMAT == "B") ~ "APP_FIRST"),
  ORDER = factor(ORDER),
  ORDER = forcats::fct_rev(ORDER)) %>% 
## FILTER OUT P11 [APP ONLY CONTROL] // P18 [BOOK ONLY CONTROL]
  filter(PID %nin% c("P11", "P18"))%>% 
## REORDER STEP FACTOR LEVELS
  mutate(
    STEP = fct_relevel(STEP, "Step 0A","Step 0B")
  ) |> 
  select(-JUNK, -MASTER_STEP) |> 
  left_join(
    lookup_step,
    by = "STEP"
  ) %>% 
  droplevels()


## RENAME INSTRUCTION TYPES
df_steps_raw$FORMAT <- fct_recode(df_steps_raw$FORMAT, 
                            "APP" = 'A', 
                            "BOOKLET" = 'B')

## DF_STEP_REPEATS
## The Step Repeat is a dual code (alongside the numbered step), applied whenever a participant meaninfully repeated the actions of a step while looking at the instructions for the step (e.g. potentially during an error recovery) 
## NOT included in PARTICIPANT count of steps (dual code would add doubles) 
## NOT included in PARTICIPANT step-level duration (dual code would add doubles)
df_step_repeats <- df_steps_raw |> 
  filter( STEP == "Step Repeat")


## DF_STEP_FLIPPING
## The 'Flipping/Tapping Through Fast code indicates when participant is engaging with instructions in order to navigate to a different point rather than meaningfully with THAT step
## NOTE flipping/tapping SHOULD be included in Participant level total step duration 
## NOTE flipping/tapping SHOULD NOT be included in Participant level step count 
df_step_flipping <- df_steps_raw |> 
  filter( STEP == "Flipping/Tapping Through Fast")


##DF_STEPS_COUNT
##data frame for time coded on a step; includes 'repeats' but not explicitly coded as repeat
## instances of each step code excluding (dual-coded) step repeat + flip
## NOTE flipping/tapping SHOULD NOT be included in Participant level step count 
## primary DF for step level analysis
df_steps_count <- df_steps_raw %>% 
  filter(STEP %nin% c("Step Repeat", "Flipping/Tapping Through Fast")) |> 
  droplevels()


## FOR STEP DURATION GRAPHS
## NOTE flipping/tapping SHOULD be included in Participant level total step duration 
df_steps_duration <- df_steps_raw %>% 
  filter(STEP %nin% c("Step Repeat")) |> 
  droplevels()

## EXPORT DF_STEPS
write.csv(df_steps_count,"data/output/df_steps_count.csv", row.names = FALSE)
write.csv(df_steps_duration,"data/output/df_steps_duration.csv", row.names = FALSE)


## CLEANUP
rm(df_steps_raw)
```

### import errors
```{r import-errors}

##import errors
## maxQDA export of all retrieved segments for the query (all documents) + (highest level Errors group code [deselect Error Pairs])
## includes error-codes + Error Types + Error Recovery
df_errors_raw <- read_csv("data/input/wip_errors.csv", col_select = 
                       c(`Document name`,
                         `Code`,
                        `Beginning`,
                        `End`
                         ),
                     show_col_types=FALSE) %>% 
    rename(
      START =  `Beginning`,
      END = `End`
    ) %>%
    separate('Document name', into = c("PID", "JAR","FORMAT"), sep = "_") %>% 
    separate('Code', into = c("BLANK","ERROR_GROUP", "ERROR_TYPE","ERROR"), sep = '>') %>% 
    ## strip weird end stuff from times
    separate(END, into = c("END", "JUNK"), sep = ',') %>% 
    separate(START, into = c("START", "JUNK"), sep = ',')  %>% 
  ## FILTER OUT P11 [APP ONLY CONTROL] // P18 [BOOK ONLY CONTROL]
  filter(PID %nin% c("P11", "P18"))%>% 
  mutate(
    PID = as_factor(PID),
    JAR = as_factor(JAR),
    FORMAT = as_factor(FORMAT),
    START = hms::as_hms(START),
    END = hms::as_hms(END),
    DURATION = END-START,
    ERROR_GROUP = as_factor(str_trim(ERROR_GROUP)),
    ERROR_TYPE = as_factor(str_trim(ERROR_TYPE)),
    ERROR = as_factor(str_trim(ERROR))
  ) %>% 
  ## CREATE ORDER FACTOR 
  mutate(
    ORDER = case_when(
      (JAR == "jar1" & FORMAT == "B") |
      (JAR == "jar2" & FORMAT == "A") ~ "BOOK_FIRST",

      (JAR == "jar1" & FORMAT == "A") |
      (JAR == "jar2" & FORMAT == "B") ~ "APP_FIRST"),
  ORDER = factor(ORDER),
  ORDER = forcats::fct_rev(ORDER)) %>% 
  select(-JUNK, -BLANK)
  
    
## RENAME INSTRUCTION TYPES
df_errors_raw$FORMAT <- fct_recode(df_errors_raw$FORMAT, 
                            "APP" = 'A', 
                            "BOOKLET" = 'B')



## participant level total error count --> sum df_errors w/o error recovery or unresolved 
## participant level unresolved error code --> sum UNRESOLVED UPON COMPLETION 


## DF_ERROR_RECOVERIES
## Error Recovery portion of time when a participant is remediating the error // 
## Unresolved Completion is dual/triple coded with the original error code if they don't recover from it (co-occurs w/ error type)
## only frequency; step codes intersection is not going to be accurate bc it will overlap with wrong step code
df_error_recoveries <- df_errors_raw %>% 
  filter(ERROR_GROUP %in% c("Error Recovery", "Unresolved Upon Completion")) %>% 
  rename(
    "RECOVERY" = "ERROR_GROUP"
  ) %>% 
  select(-ERROR_TYPE, -ERROR)

##DF_ERRORS
##data frame for number of errors; was coded while they were MAKING the error
## more precise durational data about errors should come from the error-pairs extract 
## primary DF for error analysis
df_errors <- df_errors_raw %>% 
  filter(ERROR_GROUP %nin% c("Error Recovery", "Unresolved Upon Completion")) |> 
  select(-ERROR_GROUP)
  # select(-ERROR_TYPE, -ERROR)


## TODO error-step reconcilliation
## TODO EITHER get error-pairs extract from maxqda & parse 
## OR get step code overlap from additional code columns in THIS extract 


## EXPORT DF_ERRORS
write.csv(df_errors,"data/output/df_errors.csv", row.names = FALSE)
write.csv(df_error_recoveries,"data/output/df_error_recoveries.csv", row.names = FALSE)


##CLEANUP
rm(df_errors_raw)
```

### import error-pairs
```{r import-error-pairs}


# for ones without _unresolved:
# participant eventually recovered from the error
# duration of the EE code is the time from the start of the error to when it has been completely recovered from i.e. continuous time period of: error duration+time building while error is present+error recovery time

# for ones with _unresolved:
# participant never recovered from the error
# duration of the EE code is the time spent making the error (dual coded with the error code itself). not super useful unless we can add [all steps that have a step number > that erroneous step number, maybe plus flipping/tapping after that error] to it via the code


##import errors
## maxQDA export of all retrieved segments for the query (all documents) + "error pairs" code that Zoe applied to manually keep track of error and resolutions
df_error_pairs<- read_csv("data/input/qda_error_pairs.csv", col_select = 
                      c(`Document name`,
                         `Code`,
                        `Beginning`,
                        `End`
                         ),
                     show_col_types=FALSE) %>% 
   rename(
      START =  `Beginning`,
      END = `End`
    ) %>% 
    separate('Document name', into = c("PID", "JAR","FORMAT"), sep = "_") %>% 
    separate('Code', into = c("JUNKERROR","ERRORPAIR","PIDERRORPAIR","ERRORCODE"), sep = '>') %>% 
    select(-c("JUNKERROR","ERRORPAIR","PIDERRORPAIR")) %>% 
    mutate(
      ERRORCODE= str_trim(ERRORCODE)
    ) %>% 
    separate('ERRORCODE', into = c("EE","EEPID","ERROR_CODE","ERROR_STEP","ERROR_RESOLVED"), sep = '_') %>% 
    mutate(
      STEP_CODE = str_remove(ERROR_STEP, "[abcd]$"),
      STEP_REPEAT = str_extract(ERROR_STEP, "[abcd]$"),
    ) %>% 
  left_join(
      lookup_step,   by = "STEP_CODE"
    ) %>% 
  ## HANDLE UNRESOLVED /RESOLVED 
  mutate(
        RESOLVED = ERROR_RESOLVED != "unresolved",
        RESOLVED = replace_na(RESOLVED, TRUE),
        RESOLVED = as_factor(RESOLVED)
  ) %>% 
  ## CREATE ORDER FACTOR
  mutate(
    ORDER = case_when(
      (JAR == "jar1" & FORMAT == "B") |
      (JAR == "jar2" & FORMAT == "A") ~ "BOOK_FIRST",

      (JAR == "jar1" & FORMAT == "A") |
      (JAR == "jar2" & FORMAT == "B") ~ "APP_FIRST"),
    ORDER = factor(ORDER),
    ORDER = forcats::fct_rev(ORDER)) %>% 
  ## CREATE FACTORS 
  mutate(
    PID = as_factor(PID),
    JAR = as_factor(JAR),
    START = hms::as_hms(START),
    END = hms::as_hms(END),
    DURATION = END-START,
    FORMAT = as_factor(FORMAT),
    FORMAT = fct_recode(FORMAT, "APP" = 'A', "BOOKLET" = 'B')
  ) %>% 
  left_join(
    lookup_errors,   by = "ERROR_CODE"
  ) %>%
  select(-c("EE","EEPID","ERROR_STEP","STEP_CODE", "ERROR_RESOLVED","START","END")) %>% 
  relocate(ERROR_CODE, .after = last_col())


## SUMMARIZE ERRORS PER PARTICIPANT-STEP
df_errors_summary <- df_error_pairs %>% 
  group_by(PID, JAR, FORMAT, STEP) %>% 
  dplyr::summarise(count = n())

## EXPORT DF_STEPS
write.csv(df_error_pairs,"data/output/df_error_pairs.csv", row.names = FALSE)
```





### import participants
```{r import-participants}

##import participants
## manually generated participant level file based on covariate data + participant survey
df_participants_raw <- read_csv("data/input/participants.csv", 
                     show_col_types=FALSE) |> 
  mutate(
    PID = as_factor(PID),
    Gender = as_factor(Gender),
    Experience_LEGO = as_factor(Experience_LEGO),
    Experience_DIY = as_factor(Experience_DIY),
    Childhood_LEGO = as_factor(Childhood_LEGO)
    # END = hms::as_hms(END),
  ) |> 
  ## FILTER OUT P11 [APP ONLY CONTROL] // P18 [BOOK ONLY CONTROL]
  filter(PID %nin% c("P11", "P18")) |> 
  droplevels()
  
## corsi backward span score == length of the longest sequence of colored blocks for which the participant successfully recalled at least one of the trials 

## PRIMARY PARTICIPANTS DATAFRAME
df_participants <- df_participants_raw



## CLEANUP
rm(df_participants_raw)
```

### wrangle tasks
```{r wrangle-tasks}

## CREATE lookup table
task_lookup <- df_steps_count %>%
  distinct(PID, JAR, FORMAT, ORDER)


## CREATE TASKS DATAFRAME 
## one row per participant—jar
df_tasks <- df_participants %>%
  tidyr::crossing(
    JAR = c("jar1", "jar2")
  ) %>% 
  left_join(
    task_lookup,
    by = c("PID", "JAR")
  ) %>% 
  mutate(
    JAR = as.factor(JAR)
  )%>% select(-Timestamp)



######### SUMMARIZE ERRORS BY TASK 
## summarize total errors by participant-jar
task_errors <- df_errors %>% 
  group_by(PID, JAR) %>% 
  dplyr::summarize(
    errors_jar = n()
  ) ## validated same as error-pairs df

## ADD TOTAL ERRORS TO DF_PARTICIPANTS
df_tasks <- df_tasks %>%
  left_join(
    task_errors,
    by = c("PID", "JAR")
  ) %>%
  mutate(
    errors_jar = tidyr::replace_na(errors_jar, 0)
  )

######### SUMMARIZE DURATION BY TASK 
## summarize total duration by participant-jar
task_duration <- df_steps_duration %>% 
  group_by(PID, JAR) %>% 
  dplyr::summarize(
    duration_jar = sum(as.double(DURATION))/60
  )

## ADD TOTAL ERRORS TO DF_PARTICIPANTS
df_tasks <- df_tasks %>%
  left_join(
    task_duration,
    by = c("PID", "JAR")
  ) %>%
  mutate(
    duration_jar = tidyr::replace_na(duration_jar, 0)
  )


#### TINY TASK
df_tiny_task <- df_tasks %>% 
  select(PID, JAR, FORMAT, ORDER, errors_jar, duration_jar)

## CLEANUP
rm(task_errors, task_duration)


## EXPORT df_tasks
write.csv(df_tasks,"data/output/df_tasks.csv", row.names = FALSE)
```




### wrangle participants

```{r wrangling-participants}


############## SUMMARIZE ERRORS 
## summarize total errors by participant
participant_errors <- df_errors %>% 
  group_by(PID) %>% 
  dplyr::summarize(
    errors_total = n()
  )

## ADD TOTAL ERRORS TO DF_PARTICIPANTS
df_participants <- df_participants %>%
  left_join(
    participant_errors %>% select(PID, errors_total),
    by = "PID"
  ) %>%
  mutate(
    errors_total = replace_na(errors_total, 0)
  )


############## SUMMARIZE DURATION

## sumarize total duration by participant
participant_duration <- df_steps_duration %>% 
  group_by(PID) %>% 
  dplyr::summarize(
    duration_minutes = sum(as.double(DURATION))/60
  )

## ADD TOTAL DURATION TO DF_PARTICIPANTS
df_participants <- df_participants %>%
  left_join(
    participant_duration %>% select(PID, duration_minutes),
    by = "PID"
  ) %>%
  mutate(
    duration_minutes = replace_na(duration_minutes, 0)
  )

## EXPORT df_participants
write.csv(df_participants,"data/output/df_participants.csv", row.names = FALSE)

```


### TODO import step-pair 




## STEP COUNT

### DESCRIBE participant-level
```{r steps_count_participant}

## SET DATAFRAME
df <- df_steps_count

## PRINT TABLE OF STEP COUNTS PER PARTICIPANT-JAR
title = "Number of steps per JAR per PARTICIPANT"
subtitle = "(includes repeated steps)"
(t <- table(df$PID, df$JAR) %>% 
  addmargins() %>% 
  kbl(caption = title) %>% 
  kable_classic())


## GROUPED BARCHART [COUNT STEPS X PARTICIPANT by JAR]
df %>% 
  ggplot(aes(x=PID, fill=JAR))+
    geom_bar(position="dodge") + 
  facet_wrap(~ORDER, scales = "free_x") + 
  scale_fill_brewer(palette="Paired", direction =-1) +
  theme_minimal() + 
  labs(title = "Steps per JAR per Participant",
       subtitle = "(includes repeated steps)")

## GROUPED BARCHART [COUNT STEPS X PARTICIPANT by FORMAT]
df %>% 
  ggplot(aes(x=PID, fill=FORMAT))+
    geom_bar(position="dodge") + 
   facet_wrap(~ORDER, scales = "free_x") + 
      scale_fill_brewer(palette="Set2", direction =-1) +
  theme_minimal() + 
  labs(title = "Steps per FORMAT per Participant",
       subtitle = "(includes repeated steps)")



## GROUPED BARCHART [COUNT STEPS X PARTICIPANT by JAR facet FORMAT]
g <- df %>%
  ggplot(aes(x=PID, fill=JAR))+
    geom_bar(position="dodge") +
  scale_fill_brewer(palette="Paired", direction =-1) +
  facet_wrap(~FORMAT) +
  theme_minimal() +
  labs(title = "Steps per JAR per Participant BY FORMAT",
       subtitle = "(includes step repeats)")


g
ggsave(
  filename = "figs/step_counts_by_format.svg",
  plot = g,
  device = svglite,
  width = 6,
  height = 4,
  units = "in"
)


```

### DESCRIBE jar-level
```{r steps_count_jar}

## SET DATAFRAME
df <- df_steps_count

## PRINT TABLE OF STEP COUNTS PER PARTICIPANT-JAR
title = "Number of steps per JAR per FORMAT"
subtitle = "(includes repeated steps)"
(t <- table(df$FORMAT, df$JAR) %>% 
  addmargins() %>% 
  kbl(caption = title) %>% 
  kable_classic())


## GROUPED BARCHART
## 
df %>% 
  ggplot(aes(x=FORMAT, fill=JAR))+
    geom_bar(position="dodge") + 
   facet_wrap(~ORDER, scales = "free_x") + 
  scale_fill_brewer(palette="Paired", direction =-1) +
  theme_minimal() + 
  labs(title = "Steps per FORMAT by JAR",
       subtitle = "(includes repeated steps)")

## GROUPED BARCHART 
## 
df %>% 
  ggplot(aes(x=JAR, fill=FORMAT))+
    geom_bar(position="dodge") + 
   facet_wrap(~ORDER, scales = "free_x") + 
      scale_fill_brewer(palette="Set2", direction =-1) +
  theme_minimal() + 
  labs(title = "Steps per FORMAT by JAR",
       subtitle = "(includes repeated steps)")

```

### TEST (jar-level) JAR

Is there a significant difference in number of steps PER JAR? 
```{r TEST-step-count-jar}

## SET DATAFRAME
df <- df_steps_count %>% 
  group_by(PID, JAR, FORMAT, ORDER) %>%
  dplyr::summarize( count = n())

## GGSTATSPLOT _ GROUPED WITHIN STATS
grouped_ggwithinstats(data = df, 
              x = JAR, y = count,
              grouping.var = ORDER,
              by = PID,
              type= "nonparametric",
              results.subtitle = TRUE,
              bf.message = FALSE, 
              ggtheme = ggplot2::theme_minimal())

## GGPLOT LINE GRAPH WITHIN SUBJECTS
df %>%
  ggplot(aes(JAR, count, group = PID, color=JAR)) +
  geom_line(alpha = .3) +
  scale_color_brewer(palette="Paired", direction =-1) +
  geom_point() +
  facet_wrap(~ORDER) +
  theme_minimal() + 
  labs(title = "Participant Step Count by JAR and ORDER")

## ANOVA
a <- aov_ez(
  id = "PID",
  dv = "count",
  within = c("JAR"),
  between = c("ORDER"),
  data = df
)
summary(a)


```



### TEST (jar-level) FORMAT

Is there a significant difference in number of steps PER FORMAT? 
```{r TEST-step-count-FORMAT}

## SET DATAFRAME
df <- df_steps_count %>% 
  group_by(PID, JAR, FORMAT, ORDER) %>%
  dplyr::summarize( count = n())

## GGSTATSPLOT _ GROUPED WITHIN STATS
grouped_ggwithinstats(data = df, 
              x = FORMAT, y = count,
              grouping.var = ORDER,
              by = PID,
              type= "nonparametric",
              results.subtitle = TRUE,
              bf.message = FALSE, 
              ggtheme = ggplot2::theme_minimal())

## GGPLOT LINE GRAPH WITHIN SUBJECTS
df %>%
  ggplot(aes(FORMAT, count, group = PID, color=FORMAT)) +
  geom_line(alpha = .3, color="black") +
  scale_color_brewer(palette="Set2", direction =-1) +
  geom_point() +
  facet_wrap(~ORDER) +
  theme_minimal() + 
  labs(title = "Participant Step Count by FORMAT and ORDER")

## ANOVA
a <- aov_ez(
  id = "PID",
  dv = "count",
  within = c("FORMAT"),
  between = c("ORDER"),
  data = df
)
summary(a)


```





### MODEL (participant level) STEP COUNT

What predicts number of steps per participant on each task?

```{r VIS-step-count}

## SET DATAFRAME
df <- df_steps_count %>% 
  group_by(PID, JAR, FORMAT, ORDER) %>%
  dplyr::summarize( count = n())


## PLOT RAW DATA   
## STRIP PLOT + MEAN LABEL
ggplot(df, aes(x = FORMAT, y = count, colour = FORMAT)) +
  geom_boxplot(
    aes(group = FORMAT),
    width = 0.5,
    outlier.shape = NA
  ) +
  geom_jitter(
    width = 0.1,
    alpha = 0.6,
    size = 0.5
  ) +
  # DISPLAY MEAN AS POINT
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 18,
    size = 3,
    colour = "black"
  ) +
  # MEAN LABEL
  stat_summary(
    fun = mean,
    geom = "text",
    aes(label = paste("M=",sprintf("%.2f", after_stat(y)))),
    vjust = -0.8,
    colour = "black",
    size = 3
  ) +
  facet_wrap(~ JAR) +
  theme_minimal() + 
  labs(title = "Step Count by Format & Jar",
       y = "Number of Steps")



# ######## DROP OUTLINES 
# ### DROP P10, P13
# df <- df |> filter(PID %nin% c("P10", "P13")) |> droplevels()
# 
# 
# ## PLOT RAW DATA   
# ## STRIP PLOT + MEAN LABEL
# ggplot(df, aes(x = FORMAT, y = dur, colour = FORMAT)) +
#   geom_boxplot(
#     aes(group = FORMAT),
#     width = 0.5,
#     outlier.shape = NA
#   ) +
#   geom_jitter(
#     width = 0.1,
#     alpha = 0.6,
#     size = 0.5
#   ) +
#   # DISPLAY MEAN AS POINT
#   stat_summary(
#     fun = mean,
#     geom = "point",
#     shape = 18,
#     size = 3,
#     colour = "black"
#   ) +
#   # MEAN LABEL
#   stat_summary(
#     fun = mean,
#     geom = "text",
#     aes(label = paste("M=",sprintf("%.2f", after_stat(y)))),
#     vjust = -0.8,
#     colour = "black",
#     size = 3
#   ) +
#   facet_wrap(~ JAR) +
#   theme_minimal() + 
#   labs(title = "Step Duration by Format & Jar",
#        y = "Duration (s)")



```

```{r MODEL-step-count}

## SET DATAFRAME
df <- df_steps_count %>% 
  group_by(PID, JAR, FORMAT, ORDER) %>%
  dplyr::summarize( count = n())



## MODEL 1 | Simple Main Effects
m1 <- lmer(count ~ JAR * FORMAT + (1|PID), data = df)
summary(m1)
anova(m1)
report(m1)


## PLOT MODEL ESTIMATES
 plot_model(m1, show.values= TRUE, type = "int", title = "Model Estimate (step count ~ FORMAT + JAR + (1|PID)")

## DESCRIBE MODEL VARIANCE EXPLAINED
v <- get_variance(m1)
t <- v$var.fixed + v$var.random + v$var.residual
fixed <- v$var.fixed/t * 100
random <- v$var.random/t * 100
residual <- v$var.residual/t * 100

## MODEL TABLE
m1_tab <- tidy(m1, effects = "fixed") %>%
  mutate(
    estimate  = round(estimate, 2),
    std.error = round(std.error, 2),
    statistic = round(statistic, 2),
    p.value   = ifelse(
      p.value < .001,
      "< .001",
      sprintf("= %.3f", p.value)
    )
  )
format_row <- filter(m1_tab, term == "FORMATAPP")
jar_row    <- filter(m1_tab, term == "JARjar2")
int_row    <- filter(m1_tab, term == "(Intercept)")

```

(reference level of FORMAT is BOOKLET; reference level of JAR is JAR1)

A linear mixed-effects model was fit to predict step COUNT from
FORMAT and JAR, with a random intercept for participant (PID).

The effect of FORMAT was not statistically significant, β =
`r format_row$estimate`, SE = `r format_row$std.error`, *t* =
`r format_row$statistic`, *p* `r format_row$p.value`.

In contrast, JAR significantly predicted step duration, β =
`r jar_row$estimate`, SE = `r jar_row$std.error`, *t* =
`r jar_row$statistic`, *p* `r jar_row$p.value`, indicating that steps
performed in Jar 2 took approximately `r jar_row$estimate` seconds
longer than those performed in Jar 1.

The estimated mean count in the reference condition was
`r int_row$estimate` seconds (SE = `r int_row$std.error`).

The participant-level variance was `r round(v$var.random, 2)` and the
residual variance was `r round(v$var.residual, 2)`.

*Fixed effects accounted for approximately
`r round(100 * v$var.fixed / (v$var.fixed + v$var.random + v$var.residual), 1)`%
of the total variance, participant-level differences accounted for
`r round(100 * v$var.random / (v$var.fixed + v$var.random + v$var.residual), 1)`%,
and
`r round(100 * v$var.residual / (v$var.fixed + v$var.random + v$var.residual), 1)`%
remained unexplained.*











## STEP DURATION

### DESCRIBE step distribution (all)

```{r duration-steps, warning=FALSE}

## SET DATAFRAME
df <- df_steps_duration 

## grouping by participant, jar, format to get duration by step
df_by_step <- df |> 
  group_by(PID,STEP,JAR,FORMAT) |> 
  summarise(
    STEP_DURATION = sum(DURATION)
 )

## DISTRIBUTION OF DURATION BY STEP
g <- df_by_step %>% gf_histogram(~STEP_DURATION, binwidth = 5) +
  facet_grid(JAR~FORMAT) +
  theme_minimal() +
  labs(title = "Distribution of STEP DURATION (in seconds)")

g 
ggsave(
  filename = "figs/step_duration_distribution.svg",
  plot = g,
  device = svglite,
  width = 6,
  height = 4,
  units = "in"
)

```

### DESCRIBE step distribution (by step)
```{r duration-step-level, warning=FALSE}

## SET DATAFRAME
df <- df_steps_duration 

## grouping by participant, jar, format to get duration by step
df_by_step <- df |> 
  group_by(PID,STEP,JAR,FORMAT) |> 
  summarise(
    STEP_DURATION = sum(DURATION)
 )

## DISTRIBUTION OF DURATION BY STEP
g <- df_by_step %>% gf_histogram(~STEP_DURATION, binwidth = 5, fill=~FORMAT) +
  facet_wrap(~STEP) +
  theme_minimal() +
  labs(title = "Distribution of STEP DURATION (in seconds)")

g 
ggsave(
  filename = "figs/step_level_distribution.svg",
  plot = g,
  device = svglite,
  width = 24,
  height = 24,
  units = "in"
)

```



### DESCRIBE step distribution (by complexity category)
```{r duration-step-complexity-category, warning=FALSE}

## SET DATAFRAME
df <- df_steps_duration 

## grouping by participant, jar, format to get duration by step
df_by_step <- df |> 
  group_by(PID,COMPLEXITY,JAR,FORMAT) |> 
  summarise(
    STEP_DURATION = sum(DURATION)
 )

## DISTRIBUTION OF DURATION BY STEP
g <- df_by_step %>% gf_histogram(~STEP_DURATION, fill=~FORMAT) +
  facet_wrap(~COMPLEXITY) +
  theme_minimal() +
  labs(title = "Distribution of STEP DURATION (in seconds) by complexity")

g 
ggsave(
  filename = "figs/step_category_distribution.svg",
  plot = g,
  device = svglite,
  width = 8,
  height = 8,
  units = "in"
)

```
### DESCRIBE step distribution (by complexity score)
```{r duration-step-complexity-score, warning=FALSE}

## SET DATAFRAME
df <- df_steps_duration 

## grouping by participant, jar, format to get duration by step
df_by_step <- df |> 
  group_by(PID,complexity_score,JAR,FORMAT) |> 
  summarise(
    STEP_DURATION = sum(DURATION)
 )

## DISTRIBUTION OF DURATION BY STEP
g <- df_by_step %>% gf_histogram(~STEP_DURATION, fill=~FORMAT) +
  facet_wrap(~complexity_score) +
  theme_minimal() +
  labs(title = "Distribution of STEP DURATION (in seconds) by complexity")

g 
ggsave(
  filename = "figs/step_complexityScore_distribution.svg",
  plot = g,
  device = svglite,
  width = 8,
  height = 8,
  units = "in"
)

```
### DESCRIBE participant-level

```{r steps_duration_participant}

## SET DATAFRAME
df <- df_steps_duration %>% 
  group_by(PID, JAR, FORMAT,ORDER) %>%
  summarise(
    total_duration = sum(as.numeric(DURATION), na.rm = TRUE),
    .groups = "drop"
  )

kable(df)


## GROUPED BARCHART 
df %>% 
  ggplot(aes(x=PID, y=total_duration,  fill=JAR))+
      geom_col(position = "dodge") +
  facet_wrap(~ORDER, scales = "free_x") +
  scale_fill_brewer(palette="Paired", direction =-1) +
  theme_minimal() + 
  labs(title = "Total Duration per JAR per Participant",
       subtitle = "")

## GROUPED BARCHART 
df %>% 
  ggplot(aes(x=PID, y=total_duration, fill=FORMAT))+
    geom_col(position="dodge") + 
   facet_wrap(~ORDER, scales = "free_x") + 
    scale_fill_brewer(palette="Set2", direction =-1) +
  theme_minimal() + 
  labs(title = "Total per FORMAT per Participant",
       subtitle = "")


## GROUPED BARCHART [COUNT STEPS X PARTICIPANT by JAR facet FORMAT]
g <- df %>%
  ggplot(aes(x=PID, y=total_duration, fill=JAR))+
    geom_col(position="dodge") +
  scale_fill_brewer(palette="Paired", direction =-1) +
  facet_wrap(~FORMAT) +
  theme_minimal() +
  labs(title = "Duration per JAR per Participant BY FORMAT",
       subtitle = "")

g 
ggsave(
  filename = "figs/step_duration_by_format.svg",
  plot = g,
  device = svglite,
  width = 6,
  height = 4,
  units = "in"
)
```

### DESCRIBE jar-level
```{r steps_duration_jar, warning=FALSE}


## SET DATAFRAME
df <- df_duration_by_particiapnt <- df_steps_duration |> 
  group_by(PID,JAR,FORMAT,ORDER) |> 
  summarise(
    DURATION = sum(DURATION)
 )

## GROUPED BARCHART by JAR
df %>%
    ggplot(aes(fill=JAR))+
    scale_fill_brewer(palette="Paired", direction =-1) +
    geom_bar(aes(x=FORMAT, y= DURATION), position="dodge", stat="identity") +
  facet_wrap(~ORDER) +
  theme_minimal() +
  labs(title = "Total DURATION per FORMAT per Participant",
       subtitle = "(includes step repeats)")


## GROUPED BARCHART by FORMAT
df %>%
    ggplot(aes(fill=FORMAT))+
    scale_fill_brewer(palette="Set2", direction =-1) +
    geom_bar(aes(x=JAR, y= DURATION), position="dodge", stat="identity") +
  facet_wrap(~ORDER) +
  theme_minimal() +
  labs(title = "Total DURATION by FORMAT and JAR",
       subtitle = "(includes step repeats)")
```

### TEST (jar-level) JAR -- the one with the plots

Is there a significant difference in duration of steps PER JAR? 
```{r TEST-step-duration-jar}

## SET DATAFRAME
df <- df_steps_duration %>% 
  group_by(PID, JAR, FORMAT, ORDER) %>%
  dplyr::summarize( time = as.double(sum(DURATION)))

## GGSTATSPLOT _ GROUPED WITHIN STATS
grouped_ggwithinstats(data = df, 
              x = JAR, y = time,
              grouping.var = ORDER,
              by = PID,
              type= "nonparametric",
              results.subtitle = TRUE,
              bf.message = FALSE, 
              ggtheme = ggplot2::theme_minimal())

## GGPLOT LINE GRAPH WITHIN SUBJECTS
g <- df %>%
  ggplot(aes(JAR, time, group = PID, color=FORMAT)) +
  geom_line(alpha = .3, color = "black") +
  # scale_color_brewer(palette="Paired", direction =-1) +
    scale_color_brewer(palette="Set2", direction =-1) +

  geom_point() +
  facet_wrap(~ORDER) +
  theme_minimal() + 
  labs(title = "Step DURATION by JAR and ORDER")

g 
ggsave(
  filename = "figs/linegraph_duration_jar.svg",
  plot = g,
  device = svglite,
  width = 8,
  height = 6,
  units = "in"
)


## GGPLOT LINE GRAPH WITHIN SUBJECTS
g <- df %>%
  ggplot(aes(JAR, time, group = PID, color=PID)) +
  geom_line(alpha = .3, color = "black") +
  geom_point() +
  facet_wrap(~ORDER) +
  theme_minimal() + 
  labs(title = "Step DURATION by JAR and ORDER")

g 
ggsave(
  filename = "figs/linegraph_duration_PID.svg",
  plot = g,
  device = svglite,
  width = 8,
  height = 6,
  units = "in"
)


## ANOVA
a <- aov_ez(
  id = "PID",
  dv = "time",
  within = c("JAR"),
  between = c("ORDER"),
  data = df
)
summary(a)


```



### TEST (jar-level) FORMAT
Is there a significant difference in duration of steps PER FORMAT? 
```{r TEST-step-duration-FORMAT}

## SET DATAFRAME
df <- df_steps_duration %>% 
  group_by(PID, JAR, FORMAT, ORDER) %>%
  dplyr::summarize( time = as.double(sum(DURATION)))

## GGSTATSPLOT _ GROUPED WITHIN STATS
grouped_ggwithinstats(data = df, 
              x = FORMAT, y = time,
              grouping.var = ORDER,
              by = PID,
              type= "nonparametric",
              results.subtitle = TRUE,
              bf.message = FALSE, 
              ggtheme = ggplot2::theme_minimal())

## GGPLOT LINE GRAPH WITHIN SUBJECTS
df %>%
  ggplot(aes(FORMAT, time, group = PID, color=FORMAT)) +
  geom_line(alpha = .3, color="black") +
  scale_color_brewer(palette="Set2", direction =-1) +
  geom_point() +
  facet_wrap(~ORDER) +
  theme_minimal() + 
  labs(title = "Participant Step Duration by FORMAT and ORDER")

## ANOVA
a <- aov_ez(
  id = "PID",
  dv = "time",
  within = c("FORMAT"),
  between = c("ORDER"),
  data = df
)
summary(a)


```















### MODEL STEP DURATION — INCLUDE IN THESIS

What predicts duration per step?

- TODO add fixed effect of experience
- TODO explore fixed effect of step number

```{r VIS-step-duration}

## predict step time by format and participant
df <- df_steps_duration %>% 
  mutate(
    dur = as.double(DURATION)
  )%>% filter(STEP %nin% c("Step 0A","Step 0B","Flipping/Tapping Through Fast")) %>% droplevels()

## PLOT RAW DATA   
## STRIP PLOT + MEAN LABEL
ggplot(df, aes(x = FORMAT, y = dur, colour = FORMAT)) +
  geom_boxplot(
    aes(group = FORMAT),
    width = 0.5,
    outlier.shape = NA
  ) +
  geom_jitter(
    width = 0.1,
    alpha = 0.6,
    size = 0.5
  ) +
  # DISPLAY MEAN AS POINT
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 18,
    size = 3,
    colour = "black"
  ) +
  # MEAN LABEL
  stat_summary(
    fun = mean,
    geom = "text",
    aes(label = paste("M=",sprintf("%.2f", after_stat(y)))),
    vjust = -0.8,
    colour = "black",
    size = 3
  ) +
  facet_wrap(~ JAR) +
  theme_minimal() + 
  labs(title = "Step Duration by Format & Jar",
       y = "Duration (s)")

## PLOT RAW DATA   
## STRIP PLOT + MEAN LABEL
ggplot(df, aes(x = COMPLEXITY, y = dur, colour = FORMAT)) +
  geom_boxplot(
    aes(group = COMPLEXITY),
    width = 0.5,
    outlier.shape = NA
  ) +
  geom_jitter(
    width = 0.1,
    alpha = 0.6,
    size = 0.5
  ) +
  # DISPLAY MEAN AS POINT
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 18,
    size = 3,
    colour = "black"
  ) +
  # MEAN LABEL
  stat_summary(
    fun = mean,
    geom = "text",
    aes(label = paste("M=",sprintf("%.2f", after_stat(y)))),
    vjust = -0.8,
    colour = "black",
    size = 3
  ) +
  facet_wrap(FORMAT~ JAR) +
  theme_minimal() + 
  labs(title = "Step Duration by Complexity, Format & Jar",
       y = "Duration (s)")


# ######## DROP OUTLINES 
# ### DROP P10, P13
# df <- df |> filter(PID %nin% c("P10", "P13")) |> droplevels()
# 
# 
# ## PLOT RAW DATA   
# ## STRIP PLOT + MEAN LABEL
# ggplot(df, aes(x = FORMAT, y = dur, colour = FORMAT)) +
#   geom_boxplot(
#     aes(group = FORMAT),
#     width = 0.5,
#     outlier.shape = NA
#   ) +
#   geom_jitter(
#     width = 0.1,
#     alpha = 0.6,
#     size = 0.5
#   ) +
#   # DISPLAY MEAN AS POINT
#   stat_summary(
#     fun = mean,
#     geom = "point",
#     shape = 18,
#     size = 3,
#     colour = "black"
#   ) +
#   # MEAN LABEL
#   stat_summary(
#     fun = mean,
#     geom = "text",
#     aes(label = paste("M=",sprintf("%.2f", after_stat(y)))),
#     vjust = -0.8,
#     colour = "black",
#     size = 3
#   ) +
#   facet_wrap(~ JAR) +
#   theme_minimal() + 
#   labs(title = "Step Duration by Format & Jar",
#        y = "Duration (s)")



```

```{r MODEL-step-duration}

## predict step time by format and participant
## predict step time by format and participant
df <- df_steps_duration %>% 
  mutate(
    dur = as.double(DURATION)
  )%>% filter(STEP %nin% c("Step 0A","Step 0B","Flipping/Tapping Through Fast")) %>% droplevels()

## MODEL 1 | Simple Main Effects
m1 <- lmer(dur ~ FORMAT + JAR + (1|PID), data = df)
summary(m1)
# anova(m1)
# report(m1)

## MODEL 2 | INCLUDE Complexity
m2 <- lmer(dur ~ COMPLEXITY + FORMAT + JAR + (1|PID), data = df)
summary(m2)
anova(m2)
compare_performance(m1,m2, rank = TRUE)
report(m2)
## M2 is a better fit 

## MODEL 3 | Interaction Main Effects
m3 <- lmer(dur ~ COMPLEXITY + FORMAT * JAR + (1|PID), data = df)
summary(m3)
anova(m3)
compare_performance(m1,m2,m3, rank = TRUE)
## interaction model is NOT a better fit


## BUT INTERACTION MODEL REFLECTS STRUCTURE OF THE EXPERIMENT 

## PLOT MODEL ESTIMATES
# plot_model(m1, show.values= TRUE, type = "re") # random effects
 # plot_model(m2, show.values= TRUE, type = "est", title = "Model Estimate (dur ~ COMPLEXITY + FORMAT + JAR + (1|PID)")
 # plot_model(m2, show.values= TRUE, type = "pred", title = "Model Estimate (dur ~ COMPLEXITY + FORMAT + JAR + (1|PID)")

## PLOT INTERACTION MODEL
 plot_model(m3, show.values= TRUE, type = "est", title = "Model Estimate (dur ~ COMPLEXITY + FORMAT * JAR + (1|PID)")

 plot_model(m3, show.values= TRUE, type = "int", title = "Model Estimate (dur ~ COMPLEXITY + FORMAT * JAR + (1|PID)")
 ## TODO FID INTERACTION PLOT THAT SHOWS COMPLEXITY 

## DESCRIBE MODEL VARIANCE EXPLAINED
v <- get_variance(m3)
t <- v$var.fixed + v$var.random + v$var.residual
fixed <- v$var.fixed/t * 100
random <- v$var.random/t * 100
residual <- v$var.residual/t * 100

## MODEL TABLE
m3_tab <- tidy(m3, effects = "fixed") 

## REPORT 
report(m3)

```



The participant-level variance was `r round(v$var.random, 2)` and the
residual variance was `r round(v$var.residual, 2)`.

*Fixed effects accounted for approximately
`r round(100 * v$var.fixed / (v$var.fixed + v$var.random + v$var.residual), 1)`%
of the total variance, participant-level differences accounted for
`r round(100 * v$var.random / (v$var.fixed + v$var.random + v$var.residual), 1)`%,
and
`r round(100 * v$var.residual / (v$var.fixed + v$var.random + v$var.residual), 1)`%
remained unexplained.*





## ERROR COUNT
### SETUP Error Count

```{r setup-error-counts}

## generate error counts df
error_counts_obs <- df_errors %>%
  count(PID, JAR, FORMAT, name = "n_errors")

assignments <- error_counts_obs %>%
  group_by(PID) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(
    sequence = case_when(
      (JAR == "jar1" & FORMAT == "APP") |
      (JAR == "jar2" & FORMAT == "BOOKLET") ~ "A",

      (JAR == "jar1" & FORMAT == "BOOKLET") |
      (JAR == "jar2" & FORMAT == "APP") ~ "B"
    )
  )

valid_conditions <- assignments %>%
  select(PID, sequence) %>%
  uncount(2) %>%
  group_by(PID, sequence) %>%
  mutate(
    JAR = if_else(row_number() == 1, "jar1", "jar2"),
    FORMAT = case_when(
      sequence == "A" & JAR == "jar1" ~ "APP",
      sequence == "A" & JAR == "jar2" ~ "BOOKLET",
      sequence == "B" & JAR == "jar1" ~ "BOOKLET",
      sequence == "B" & JAR == "jar2" ~ "APP"
    )
  ) %>%
  ungroup() %>%
  select(PID, JAR, FORMAT)

error_counts <- valid_conditions %>%
  left_join(
    error_counts_obs,
    by = c("PID", "JAR", "FORMAT")
  ) %>%
  mutate(
    n_errors = replace_na(n_errors, 0),
    JAR = as.factor(JAR),
    FORMAT = as.factor(FORMAT)
  ) %>%
  arrange(PID, JAR) 

df_error_counts <- error_counts %>% 
## CREATE ORDER FACTOR 
  mutate(
    ORDER = case_when(
      (JAR == "jar1" & FORMAT == "BOOKLET") |
      (JAR == "jar2" & FORMAT == "APP") ~ "BOOK_FIRST",

      (JAR == "jar1" & FORMAT == "APP") |
      (JAR == "jar2" & FORMAT == "BOOKLET") ~ "APP_FIRST"),
  ORDER = factor(ORDER),
  ORDER = forcats::fct_rev(ORDER)) %>% 
  droplevels()

rm(error_counts_obs, valid_conditions, error_counts)
```

### DESCRIBE Error Count (Participant)

```{r count-errors}
df <- df_error_counts


## GROUPED BARCHART 
df %>% 
  ggplot(aes(x=PID, fill=JAR, y = n_errors))+
    geom_col(position = "dodge") +
    facet_wrap(~ORDER, scales = "free_x") + 
    scale_fill_brewer(palette="Paired", direction =-1) +
    theme_minimal() + 
    labs(title = "Errors per JAR per Participant")

## GROUPED BARCHART 
df %>% 
  ggplot(aes(x=PID, fill=FORMAT, y = n_errors))+
    geom_col(position = "dodge") +
    facet_wrap(~ORDER, scales = "free_x") + 
    scale_fill_brewer(palette="Set2", direction =-1) +
    theme_minimal() + 
    labs(title = "Errors per JAR per Participant")

```


### DESCRIBE Error Count (Step) —- VIS ERROR BY STEP

## TODO RECONCILE error pair summary of errors per jar/app with error recovery
## TODO add missing zeros to df_errors_summary 
```{r count-errors_step}
df <- df_error_pairs

df2 <- df_errors_summary


## GROUPED BARCHART 
df2 %>% 
  ggplot(aes(x=STEP, fill=FORMAT ))+
    geom_bar(position = "dodge") +
    facet_wrap(~JAR) + 
    # facet_wrap(~ORDER, scales = "free_x") + 
    # scale_fill_brewer(palette="Paired", direction =-1) +
    theme_minimal()
# + 
    # labs(title = "Errors per JAR per Participant")


## GROUPED BARCHART 
df %>% 
  ggplot(aes(x=COMPLEXITY, fill=FORMAT ))+
    geom_bar(position = "dodge") +
    facet_wrap(~JAR) + 
    # facet_wrap(~ORDER, scales = "free_x") + 
    # scale_fill_brewer(palette="Paired", direction =-1) +
    theme_minimal()
# + 
    # labs(title = "Errors per JAR per Participant")



# ## GROUPED BARCHART 
# df %>% 
#   ggplot(aes(x=PID, fill=FORMAT, y = n_errors))+
#     geom_col(position = "dodge") +
#     facet_wrap(~ORDER, scales = "free_x") + 
#     scale_fill_brewer(palette="Set2", direction =-1) +
#     theme_minimal() + 
#     labs(title = "Errors per JAR per Participant")

```


### TEST Error Count JAR
```{r test-error-count-JAR}
df <- df_error_counts

## GGSTATSPLOT _ GROUPED WITHIN STATS
grouped_ggwithinstats(data = df, 
              x = JAR, y = n_errors,
              grouping.var = ORDER,
              by = PID,
              type= "nonparametric",
              results.subtitle = TRUE,
              bf.message = FALSE, 
              ggtheme = ggplot2::theme_minimal())

## GGPLOT LINE GRAPH WITHIN SUBJECTS
df %>%
  ggplot(aes(JAR, n_errors, group = PID, color=JAR)) +
  geom_line(alpha = .3) +
  scale_color_brewer(palette="Paired", direction =-1) +
  geom_point() +
  facet_wrap(~ORDER) +
  theme_minimal() + 
  labs(title = "Error Count by JAR and ORDER")

## ANOVA
a <- aov_ez(
  id = "PID",
  dv = "n_errors",
  within = c("JAR"),
  between = c("ORDER"),
  data = df
)
summary(a)


```

### TEST Error Count FORMAT
```{r test-error-count-FORMAT}
df <- df_error_counts

## GGSTATSPLOT _ GROUPED WITHIN STATS
grouped_ggwithinstats(data = df, 
              x = FORMAT, y = n_errors,
              grouping.var = ORDER,
              by = PID,
              type= "nonparametric",
              results.subtitle = TRUE,
              bf.message = FALSE, 
              ggtheme = ggplot2::theme_minimal())

## GGPLOT LINE GRAPH WITHIN SUBJECTS
df %>%
  ggplot(aes(FORMAT, n_errors, group = PID, color=JAR)) +
  geom_line(alpha = .3, color="black") +
  scale_fill_brewer(palette="Set2", direction =-1) +
  geom_point() +
  facet_wrap(~ORDER) +
  theme_minimal() + 
  labs(title = "Error Count by JAR and ORDER")

## ANOVA
a <- aov_ez(
  id = "PID",
  dv = "n_errors",
  within = c("FORMAT"),
  between = c("ORDER"),
  data = df
)
summary(a)


```


### MODEL Error Count
What predicts number of errors?

```{r error-vis}

## set dataframe
df <- df_error_counts

df %>% ggplot(
       aes(x = FORMAT,
           y = n_errors,
           colour = JAR)) +
  geom_boxplot(
    aes(group = FORMAT),
    outlier.shape = NA
  ) +
  geom_jitter(width = 0.08, alpha = 0.6) +
    # DISPLAY MEAN AS POINT
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 18,
    size = 3,
    colour = "black"
  ) +
  # MEAN LABEL
  stat_summary(
    fun = mean,
    geom = "text",
    aes(label = paste("M=",sprintf("%.2f", after_stat(y)))),
    vjust = -0.8,
    colour = "black",
    size = 3
  ) +
  facet_wrap(~ JAR) +
  theme_minimal() + 
  labs(title = "Error Count by Format & Jar", 
       y = "Number of Errors")




# ######## DROP OUTLINES 
# ### DROP P10, P13
# # df <- df |> filter(PID %nin% c("P10", "P13")) |> droplevels()
# 
# 
# ### removed 
# ggplot(df,
#        aes(x = FORMAT,
#            y = n_errors,
#            colour = JAR)) +
#   geom_boxplot(
#     aes(group = FORMAT),
#     outlier.shape = NA
#   ) +
#   geom_jitter(width = 0.08, alpha = 0.6) +
#     # DISPLAY MEAN AS POINT
#   stat_summary(
#     fun = mean,
#     geom = "point",
#     shape = 18,
#     size = 3,
#     colour = "black"
#   ) +
#   # MEAN LABEL
#   stat_summary(
#     fun = mean,
#     geom = "text",
#     aes(label = paste("M=",sprintf("%.2f", after_stat(y)))),
#     vjust = -0.8,
#     colour = "black",
#     size = 3
#   ) +
#   facet_wrap(~ JAR) +
#   theme_minimal() + 
#   labs(title = "Error Count by Format & Jar", 
#        y = "Number of Errors")
# 
# 
# ## INDIVIDUAL DIFFERENCES BY JAR
# ggplot(df, aes(x = JAR, y = n_errors, group = PID)) +
#   geom_line(alpha = 0.35) +
#   geom_point(size = 2, alpha = 0.8) +
#   theme_bw() +
#   labs(
#     x = "Jar",
#     y = "Error Count"
#   )+ 
#   theme_minimal() + 
#   labs(title = "Error Count by JAR",
#                          subtitle = "(lines connect PIDs)")
# 
# ## INDIVIDUAL DIFFERENCES BY JAR
# ggplot(df, aes(x = FORMAT, y = n_errors, group = PID)) +
#   geom_line(alpha = 0.35) +
#   geom_point(size = 2, alpha = 0.8) +
#   theme_bw() +
#   labs(
#     x = "Format",
#     y = "Error Count"
#   )+
#   theme_minimal() + 
#   labs(title = "Error Count by FORMAT",
#                          subtitle = "(lines connect PIDs)")


```

```{r model-error-poisson}

## df = error counts dataframe
df <- df_error_counts 

######## DROP OUTLINES 
### DROP P10, P13
# df <- df |> filter(PID %nin% c("P10", "P13")) |> droplevels()

## MODEL 1 | Poisson model for count data
m_pois <- glmer(
  n_errors ~ FORMAT + JAR + (1|PID),
  family = poisson,
  data = df
)
summary(m_pois)
check_overdispersion(m_pois)
# anova(m_pois)
# report(m_pois)







## PLOT MODEL ESTIMATES
# plot_model(m_pois, show.values= TRUE, type = "re") # random effects
plot_model(m_pois, show.values= TRUE, type = "est", title = "Model Estimate (n_errors ~ FORMAT + JAR + (1|PID), family = poisson")


## MODEL TABLE
m_pois_tab <- tidy(m_pois, effects = "fixed") %>%
  mutate(
    beta = round(estimate, 2),
    se   = round(std.error, 2),
    z    = round(statistic, 2),
    p    = ifelse(p.value < .001, "< .001", paste0("= ", round(p.value, 3))),
    irr  = round(exp(estimate), 2),
    pct_change = round((exp(estimate) - 1) * 100, 0)
  )

format_booklet <- m_pois_tab %>% filter(term == "FORMATBOOKLET")
jar2           <- m_pois_tab %>% filter(term == "JARjar2")
intercept      <- m_pois_tab %>% filter(term == "(Intercept)")

## RANDOM EFFECT
re_var <- as.data.frame(VarCorr(m_pois)) %>%
  filter(grp == "PID") %>%
  pull(vcov)

re_sd <- as.data.frame(VarCorr(m_pois)) %>%
  filter(grp == "PID") %>%
  pull(sdcor)

## OVERDISPERSION
od <- performance::check_overdispersion(m_pois)

## DESCRIBE MODEL VARIANCE EXPLAINED
v_pois <- get_variance(m_pois,   tolerance = 1e-12)
total_var <- v_pois$var.fixed +
             v_pois$var.random +
             v_pois$var.residual

fixed_pct <- 100 * v_pois$var.fixed / total_var
random_pct <- 100 * v_pois$var.random / total_var
resid_pct <- 100 * v_pois$var.residual / total_var

```

A Poisson generalized linear mixed-effects model was fit to predict error count from FORMAT and JAR, with a random intercept for participant (PID). A significant effect of JAR was observed, with Jar 2 associated with higher error counts than Jar 1 (β = `r jar2$beta`, SE = `r jar2$se`, *z* = `r jar2$z`, *p* `r jar2$p`). Exponentiating the coefficient indicated that expected error counts were approximately `r jar2$pct_change`% higher in Jar 2 than in Jar 1 (IRR = `r jar2$irr`). The effect of FORMAT was not statistically significant (β = `r format_booklet$beta`, SE = `r format_booklet$se`, *z* = `r format_booklet$z`, *p* `r format_booklet$p`), although error counts were estimated to be approximately `r format_booklet$pct_change`% higher for BOOKLET than APP (IRR = `r format_booklet$irr`). The participant-level random intercept variance was `r round(re_var, 2)` (SD = `r round(re_sd, 2)`). 

Variance decomposition indicated that fixed effects accounted for approximately `r round(fixed_pct, 1)`% of the total variance, participant-level variability accounted for `r round(random_pct, 1)`%, and `r round(resid_pct, 1)`% remained unexplained. 

An overdispersion diagnostic found no evidence that the Poisson assumption was violated (dispersion ratio = `r round(od$dispersion_ratio, 2)`, *p* = `r ifelse(od$p_value < .001, "< .001", paste0("= ", round(od$p_value, 3)))`).

```{r model-error-negativeBIONOM}
# ## MODEL 2 | Negative binomial model for overdispersed count data
# m_nb <- glmmTMB(
#   n_errors ~ FORMAT + JAR + (1|PID),
#   family = nbinom2, 
#   data = error_counts
# )
# summary (m_nb)
# report(m_nb)
# 
# ## PLOT MODEL ESTIMATES
# plot_model(m_nb, values = TRUE, type = "est",
#            title = "Model Prediction for (n_errors n_errors ~ FORMAT + JAR + (1|PID) [family = nbinom2]")
# 
# 
# ## MODEL TABLE
# m_nb_tab <- tidy(m_nb, effects = "fixed") %>%
#   mutate(
#     beta = round(estimate, 2),
#     se   = round(std.error, 2),
#     z    = round(statistic, 2),
#     p    = ifelse(p.value < .001, "< .001", paste0("= ", round(p.value, 3)))
#   )
# 
# #m_nb_tab
# format_app <- m_nb_tab %>% filter(term == "FORMATAPP")
# jar2       <- m_nb_tab %>% filter(term == "JARjar2")
# re_var <- as.data.frame(VarCorr(m_nb)$cond$PID)[1, 1]
# 
# ## DESCRIBE MODEL VARIANCE EXPLAINED
# v_nb <- get_variance(m_nb,   tolerance = 1e-12)
# total_var <- v_nb$var.fixed +
#              v_nb$var.random +
#              v_nb$var.residual
# 
# fixed_pct <- 100 * v_nb$var.fixed / total_var
# random_pct <- 100 * v_nb$var.random / total_var
# resid_pct <- 100 * v_nb$var.residual / total_var


# A negative binomial generalized linear mixed-effects model was fit to
# predict error counts from FORMAT and JAR, with a random intercept for
# participant (PID). Neither predictor was significantly associated with
# error count. Relative to the reference format, the APP format was
# associated with a non-significant reduction in expected errors (β =
# `r format_app$beta`, SE = `r format_app$se`, z = `r format_app$z`, p
# `r format_app$p`). Similarly, Jar 2 was associated with a
# non-significant increase in expected errors relative to Jar 1 (β =
# `r jar2$beta`, SE = `r jar2$se`, z = `r jar2$z`, p `r jar2$p`). The
# participant-level random-intercept variance was `r signif(re_var, 3)`,
# indicating little evidence of systematic between-participant differences
# in baseline error rates.
# 
# Variance decomposition indicated that fixed effects accounted for approximately `r round(fixed_pct,2)`% of the total variance, participant-level variability accounted for `r  format(random_pct, scientific=FALSE)`%, and `r round(resid_pct,2)`% remained unexplained.
```





## ERROR TYPE

### DESCRIBE Error Type

```{r}

## SET ERRORS DF
df <- df_errors

## GROUPED BARCHART [COUNT ERRORS X TYPE X FORMAT X ]
df %>% 
  ggplot(aes(x=FORMAT, fill=ERROR_TYPE))+
    geom_bar(position="dodge") + 
  theme_minimal() + 
  labs(title = "Errors by FORMAT and TYPE")

## FACETED GROUPED BARCHART [COUNT ERRORS X TYPE X FORMAT X ]
df %>% 
  ggplot(aes(x=FORMAT, fill=ERROR_TYPE))+
    geom_bar(position="dodge") + 
  facet_wrap(~JAR) + 
  theme_minimal() + 
  labs(title = "Errors by FORMAT and TYPE")



## ZOES DETAIL GRAPH
g <- df %>% 
  ggplot(aes(x=ERROR_TYPE, fill=ERROR))+
    geom_bar(stat="count") + 
  facet_wrap(~FORMAT) +
  theme_minimal() + 
  labs(title = "Errors by FORMAT and TYPE")

g 
ggsave(
  filename = "figs/errors_by_format_type.svg",
  plot = g,
  device = svglite,
  width = 10,
  height = 4,
  units = "in"
)



```



## ERROR RECOVERY

### DESCRIBE Error Recovery

```{r count-recoveries}
df <- df_error_recoveries

## GROUPED BARCHART []
g <- df %>% 
  ggplot(aes(x=FORMAT, fill=RECOVERY))+
    geom_bar() + 
  scale_fill_brewer(palette="Paired", direction =1) +
  facet_wrap(~JAR) + 
  theme_minimal() + 
  labs(title = "Errors RECOVERY by FORMAT")

g 
ggsave(
  filename = "figs/errors_recovery.svg",
  plot = g,
  device = svglite,
  width = 6,
  height = 4,
  units = "in"
)

```
### MODEL Error Recovery

```{r errors-recovery}

## one row per error
df <- df_error_recoveries |> 
  droplevels() |> 
   mutate(RECOVERY = fct_rev(RECOVERY))

m1 <- glmer(
  RECOVERY ~ FORMAT + JAR + (1 | PID),
  data = df,
  family = binomial(link = "logit")
)
# summary(m1)

m2 <- glmer(
  RECOVERY ~ FORMAT * JAR + (1 | PID),
  data = df,
  family = binomial(link = "logit")
)
summary(m2)

# compare_performance(m1,m2, rank = TRUE)


# report(m1)
report(m2)


plot_model(m2, type = "est", title = "error recovery ~ JAR * FORMAT", show.value = TRUE, show.p=TRUE)
plot_model(m2, type = "int", title = "error recovery ~ JAR * FORMAT")


```





## SPEED-ACCURACY

### DESCRIBE Jar-level 

What is the relationship between a participant's speed and accuracy on the tasks?
```{r, warning=FALSE}
## SET DATAFRAME
df <- df_tiny_task


## SCATTERPLOT
g <- df %>% ggplot(aes(x= duration_jar, y = errors_jar, color=FORMAT)) +
  geom_jitter(alpha=0.5) + 
  scale_color_brewer(palette="Set2", direction =-1) +
  # geom_smooth(method = "lm", se = TRUE) + # linear regression
  geom_smooth(
  method = "glm",
  method.args = list(family = poisson),
  se = TRUE
 ) + 
  # facet_wrap(~JAR) + 
  theme_minimal() +
  labs(title = "Participant SPEED X ACCURACY")

g
ggsave(
  filename = "figs/speed_accuracy_JAR.svg",
  plot = g,
  device = svglite,
  width = 6,
  height = 4,
  units = "in"
)



## SCATTERPLOT
df %>% ggplot(aes(x= errors_jar, y = duration_jar, color=FORMAT)) +
  geom_point(alpha=0.5) + 
   # geom_smooth(method = "lm", se = TRUE) + # linear regression
  geom_smooth(
  method = "glm",
  method.args = list(family = poisson),
  se = TRUE
 ) + 
  scale_color_brewer(palette="Set2", direction =-1) +
  facet_wrap(~JAR) + 
  theme_minimal() + 
  labs(title = "Participant SPEED X ACCURACY")


## SCATTERPLOT
g <- df %>% ggplot(aes(x= duration_jar, y = errors_jar, color=FORMAT)) +
  geom_point(alpha=0.5) + 
  scale_color_brewer(palette="Set2", direction =-1) +
   # geom_smooth(method = "lm", se = TRUE) + # linear regression
  geom_smooth(
  method = "glm",
  method.args = list(family = poisson),
  se = TRUE
 ) + 
  facet_wrap(~FORMAT) + 
  theme_minimal() + 
  labs(title = "Participant SPEED X ACCURACY",
       caption="(poisson regression)") 
  
g
ggsave(
  filename = "figs/speed_accuracy_FORMAT_FACET.svg",
  plot = g,
  device = svglite,
  width = 6,
  height = 4,
  units = "in"
)


## SCATTERPLOT
g <- df %>% ggplot(aes(x= duration_jar, y = errors_jar, color=JAR)) +
  geom_point(alpha=0.5) + 
  scale_color_brewer(palette="Set2", direction =-1) +
   # geom_smooth(method = "lm", se = TRUE) + # linear regression
  geom_smooth(
  method = "glm",
  method.args = list(family = poisson),
  se = TRUE
 ) + 
  facet_wrap(~FORMAT) + 
  theme_minimal() + 
  labs(title = "Participant SPEED X ACCURACY",
       caption="(poisson regression)") 
  
g
ggsave(
  filename = "figs/speed_accuracy_JAR_FORMAT_FACET.svg",
  plot = g,
  device = svglite,
  width = 6,
  height = 4,
  units = "in"
)
```


### MODEL Jar-level
```{r}

df <- df_tasks

m1 <- lmer(duration_jar ~ errors_jar + FORMAT + JAR + (1|PID), data = df)
summary(m1)
report(m1)

plot_model(m1, type="est", show.values = TRUE, show.p = TRUE, title = "duration_jar ~ errors + FORMAT + JAR + (1|PID)")
plot_model(m1, type = "pred")
```

## TODO JAR-LEVEL TABLE
## WIP


### TODO Predict Error TYPE by FORMAT

```{r }

# df <- df_errors
# 
# ## PREDICT TYPE by FORMAT 
# 
# library(glmmTMB)
# 
# m1 <- glmmTMB(
#   ERROR_TYPE ~ FORMAT + JAR + (1 | PID),
#   data = df,
#   family = multinomial()
# )
# 
# 
# library(brms)
# 
# model <- brm(
#   ERROR_TYPE ~ FORMAT + JAR + (1 | PID),
#   data = df,
#   family = categorical()
# )
# 
# 
# 
# install.packages("mclogit")
# library(mclogit)
# 
# model <- mblogit(
#   ERROR_TYPE ~ FORMAT + JAR,
#   random = ~ 1 | PID,
#   data = df
# )


```






## STASH

```{r stash}

## REFERENCE CONDITIONAL MUTATE SYNTAX
 # mutate(grade = case_when(
 #    score >= 90 ~ "A",
 #    score >= 80 ~ "B",
 #    TRUE ~ "C"  # Default value
 #  ))



```
