---
title: "x"
author: "Amy & Zoe"
date: "2026-05-06"
output:
  html_document:
    theme: cosmo
    code_folding: hide
    fig_caption: yes
    number_sections: no
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    toc_depth: 6
  pdf_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
font-family: DejaVu Sans
mainfont: DejaVu Sans
editor_options: 
  markdown: 
    wrap: 72
---

## SETUP

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) #all the things
library(dplyr) #all the things
library(lubridate) #timey-wimey
library(ggformula) #regression syntax viz
library(Hmisc) # %nin% operator

```

```{r import-steps}

df_steps <- read_csv("data/wip_steps.csv", col_select = 
                       c(`Document name`,
                         `Code`,
                        `Beginning`,
                        `End`
                         ),
                     show_col_types=FALSE) %>% 
    rename(
      START =  `Beginning`,
      END = `End`
    ) %>%
    separate('Document name', into = c("PID", "JAR","FORMAT"), sep = "_") %>% 
    separate('Code', into = c("MASTER_STEP", "STEP"), sep = '>') %>% 
    ## strip weird end stuff from times
    separate(END, into = c("END", "JUNK"), sep = ',') %>% 
    separate(START, into = c("START", "JUNK"), sep = ',') %>% 
  mutate(
    PID = as_factor(PID),
    JAR = as_factor(JAR),
    FORMAT = as_factor(FORMAT),
    STEP = as_factor(STEP),
    MASTER_STEP = as_factor(MASTER_STEP),
    START = hms::as_hms(START),
    END = hms::as_hms(END),
    DURATION = END-START
  ) %>% select(-JUNK)

## RENAME INSTRUCTION TYPES
df_steps$FORMAT <- fct_recode(df_steps$FORMAT, 
                            "APP" = 'A', 
                            "BOOK" = 'B')

## REFERENCE CONDITIONAL MUTATE SYNTAX
 # mutate(grade = case_when(
 #    score >= 90 ~ "A",
 #    score >= 80 ~ "B",
 #    TRUE ~ "C"  # Default value
 #  ))


```

```{r import-errors}

##import errors
df_errors <- read_csv("data/wip_errors.csv", col_select = 
                       c(`Document name`,
                         `Code`,
                        `Beginning`,
                        `End`
                         ),
                     show_col_types=FALSE) %>% 
    rename(
      START =  `Beginning`,
      END = `End`
    ) %>%
    separate('Document name', into = c("PID", "JAR","FORMAT"), sep = "_") %>% 
    separate('Code', into = c("BLANK","ERROR_GROUP", "ERROR_TYPE","ERROR"), sep = '>') %>% 
    ## strip weird end stuff from times
    separate(END, into = c("END", "JUNK"), sep = ',') %>% 
    separate(START, into = c("START", "JUNK"), sep = ',') %>% 
  mutate(
    PID = as_factor(PID),
    JAR = as_factor(JAR),
    FORMAT = as_factor(FORMAT),
    # STEP = as_factor(STEP),
    # MASTER_STEP = as_factor(MASTER_STEP),
    START = hms::as_hms(START),
    END = hms::as_hms(END),
    DURATION = END-START,
    BLANK = as_factor(str_trim(BLANK)),
    ERROR_GROUP = as_factor(str_trim(ERROR_GROUP)),
    ERROR_TYPE = as_factor(str_trim(ERROR_TYPE)),
    ERROR = as_factor(str_trim(ERROR))
  ) %>% select(-JUNK, -BLANK)
  

## RENAME INSTRUCTION TYPES
df_errors$FORMAT <- fct_recode(df_errors$FORMAT, 
                            "APP" = 'A', 
                            "BOOK" = 'B')


## get error recoveries-non-recoveries 
df_recoveries <- df_errors %>% 
  filter(ERROR_GROUP %in% c("Error Recovery", "Unresolved Upon Completion")) %>% 
  rename(
    "RECOVERY" = "ERROR_GROUP"
  ) %>% 
  select(-ERROR_TYPE, -ERROR)

## get just top level error codes
df_groups <- df_errors %>% 
  filter(ERROR_GROUP %nin% c("Error Recovery", "Unresolved Upon Completion")) 
  # select(-ERROR_TYPE, -ERROR)



## REFERENCE CONDITIONAL MUTATE SYNTAX
 # mutate(grade = case_when(
 #    score >= 90 ~ "A",
 #    score >= 80 ~ "B",
 #    TRUE ~ "C"  # Default value
 #  ))


```


## STEPS


### COUNT STEPS 
```{r count-steps}

print('Number of steps per jar per participant')
table(df_steps$PID, df_steps$JAR)


## GROUPED BARCHART [COUNT STEPS X PARTICIPANT by JAR]
df_steps %>% 
  ggplot(aes(x=PID, fill=JAR))+
    geom_bar(position="dodge") + 
  theme_minimal() + 
  labs(title = "Steps per JAR per Participant",
       subtitle = "(includes step repeats)")

## GROUPED BARCHART [COUNT STEPS X PARTICIPANT by JAR facet FORMAT]
df_steps %>% 
  ggplot(aes(x=PID, fill=JAR))+
    geom_bar(position="dodge") + 
  facet_wrap(~FORMAT) + 
  theme_minimal() + 
  labs(title = "Steps per JAR per Participant BY FORMAT",
       subtitle = "(includes step repeats)")


```

### DURATION STEPS 
```{r duration-steps}

df_steps %>% gf_histogram(~DURATION) +
  facet_grid(JAR~FORMAT) + 
  theme_minimal() + 
  labs(title = "Distribution of STEP DURATION")


## GROUPED BARCHART [COUNT STEPS X PARTICIPANT by JAR]
df_steps %>% 
  ggplot(aes(x=PID, fill=JAR))+
    geom_bar(position="dodge") + 
  theme_minimal() + 
  labs(title = "Steps per JAR per Participant",
       subtitle = "(includes step repeats)")

## GROUPED BARCHART [COUNT STEPS X PARTICIPANT by JAR facet FORMAT]
df_steps %>% 
  ggplot(aes(x=PID, fill=JAR))+
    geom_bar(position="dodge") + 
  facet_wrap(~FORMAT) + 
  theme_minimal() + 
  labs(title = "Steps per JAR per Participant BY FORMAT",
       subtitle = "(includes step repeats)")


```






### DURATION FORMATS
```{r duration-formats}

df <- df_steps %>% 
  group_by(PID, FORMAT,JAR) %>% 
  summarise(
    time = sum(DURATION)
  )

# df %>% gf_histogram(~time) +
#   facet_wrap(~FORMAT) + 
#   theme_minimal()

df %>% ggplot(aes(x=FORMAT, y=time)) +
  geom_jitter(alpha=0.4, width=0.00, aes(color=JAR)) + 
  geom_line(aes(group=PID))+
  theme_minimal() + 
  labs(title = "JAR duration by FORMAT",
       subtitle="line indicates participant")
  

```




## ERRORS
### COUNT ERRORS 
```{r count-errors}
df <- df_groups

print('Number of errors per jar per participant')
table(df$PID, df$JAR)


## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT by JAR]
df %>% 
  ggplot(aes(x=PID, fill=JAR))+
    geom_bar(position="dodge") + 
  theme_minimal() + 
  labs(title = "Errors per JAR per Participant")

## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT by JAR facet FORMAT]
df %>% 
  ggplot(aes(x=PID, fill=JAR))+
    geom_bar(position="dodge") + 
  facet_wrap(~FORMAT) + 
  theme_minimal() + 
  labs(title = "Errors per JAR per Participant BY FORMAT")


## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT by JAR facet FORMAT]
df %>% 
  ggplot(aes(x=PID, fill=FORMAT))+
    geom_bar(position="dodge") + 
  facet_wrap(~ERROR_TYPE) + 
  theme_minimal() + 
  labs(title = "Errors per FORMAT BY TYPE")

## GROUPED BARCHART [COUNT ERRORS X TYPE X FORMAT X ]
df %>% 
  ggplot(aes(x=FORMAT, fill=ERROR_TYPE))+
    geom_bar(position="dodge") + 
  theme_minimal() + 
  labs(title = "Errors by FORMAT and TYPE")



## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT facet FORMAT X JAR]
df %>% 
  ggplot(aes(x=PID, fill=ERROR_TYPE))+
    geom_bar() + 
  facet_wrap(JAR~FORMAT) + 
  theme_minimal() + 
  labs(title = "Errors per JAR per Participant BY FORMAT")




```

### COUNT ERROR RECOVERY 
```{r count-recoveries}
df <- df_recoveries

print('Number of recovery type per jar per participant')
table(df$PID, df$JAR, df$RECOVERY)


  ## GROUPED BARCHART [COUNT RECOVERIES X by JAR]
df %>% 
  ggplot(aes(x=PID, fill=RECOVERY))+
    geom_bar(position="dodge") + 
  facet_grid(FORMAT~JAR) +
  theme_minimal() + 
  labs(title = "Recoveries per JAR per Participant")

## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT by JAR facet FORMAT]
df %>% 
  ggplot(aes(x=RECOVERY, fill=FORMAT))+
    geom_bar(position="dodge") + 
  # facet_wrap(FORMAT) + 
  theme_minimal() + 
  labs(title = "Errors RECOVERY by FORMAT")
```


## QUESTIONS 



### STRATEGY

#### organization 

#### strategy X errors
- Will pre-sorting by jar result in less piece selection errors?



- 'flip everything up at start' less piece selection errors?
- does model matching correspond with less (spatial transformation) errors?


### SPEED/ACCURACY 

