---
title: "Lego Assembly Thesis Analysis"
author: "Amy Rae Fox & Zoe Kothari"
date: "2026-05-06"
output:
  html_document:
    theme: cosmo
    code_folding: hide
    fig_caption: yes
    number_sections: no
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    toc_depth: 6
  pdf_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
font-family: DejaVu Sans
mainfont: DejaVu Sans
editor_options: 
  markdown: 
    wrap: 72
---

## SETUP

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) #all the things
library(dplyr) #all the things 
library(lubridate) #timey-wimey
library(ggformula) #regression syntax viz
library(Hmisc) # %nin% operator
library(svglite)


```

```{r import-steps}

## DF_STEPS_RAW
## maxQDA export of all retrieved segments for the query (all documents) + (highest level step code [includes each numbered step + Step Repeat + Flipping/Tapping Through Fast])
## NOTE: need to handle Step Repeat + Flipping/Tapping Through Fast seperately 
df_steps_raw <- read_csv("data/input/wip_steps.csv", col_select = 
                       c(`Document name`,
                         `Code`,
                        `Beginning`,
                        `End`
                         ),
                     show_col_types=FALSE) %>% 
    rename(
      START =  `Beginning`,
      END = `End`
    ) %>%
    separate('Document name', into = c("PID", "JAR","FORMAT"), sep = "_") %>% 
    separate('Code', into = c("MASTER_STEP", "STEP"), sep = '>') %>% 
    ## strip weird end stuff from times
    separate(END, into = c("END", "JUNK"), sep = ',') %>% 
    separate(START, into = c("START", "JUNK"), sep = ',') %>% 
  mutate(
    PID = as_factor(PID),
    JAR = as_factor(JAR),
    FORMAT = as_factor(FORMAT),
    # ERROR_GROUP = as_factor(str_trim(ERROR_GROUP)),
    STEP = as_factor(str_trim(STEP)),
    # MASTER_STEP = as_factor(MASTER_STEP),
    START = hms::as_hms(START),
    END = hms::as_hms(END),
    DURATION = END-START
  ) |> 
## FILTER OUT P11 [APP ONLY CONTROL] // P18 [BOOK ONLY CONTROL]
  filter(PID %nin% c("P11", "P18"))%>% 
## REORDER STEP FACTOR LEVELS
  mutate(
    STEP = fct_relevel(STEP, "Step 0A","Step 0B")
  ) |> 
  select(-JUNK, -MASTER_STEP) |> 
  droplevels()


## RENAME INSTRUCTION TYPES
df_steps_raw$FORMAT <- fct_recode(df_steps_raw$FORMAT, 
                            "APP" = 'A', 
                            "BOOKLET" = 'B')

## DF_STEP_REPEATS
## The Step Repeat is a dual code (alongside the numbered step), applied whenever a participant meaninfully repeated the actions of a step while looking at the instructions for the step (e.g. potentially during an error recovery) 
## NOT included in PARTICIPANT count of steps (dual code would add doubles) 
## NOT included in PARTICIPANT step-level duration (dual code would add doubles)
df_step_repeats <- df_steps_raw |> 
  filter( STEP == "Step Repeat")


## DF_STEP_FLIPPING
## The 'Flipping/Tapping Through Fast code indicates when participant is engaging with instructions in order to navigate to a different point rather than meaningfully with THAT step
## TODO flipping/tapping SHOULD be included in Participant level total step duration 
## TODO flipping/tapping SHOULD NOT be included in Participant level step count 
df_step_flipping <- df_steps_raw |> 
  filter( STEP == "Flipping/Tapping Through Fast")


##DF_STEPS
##data frame for time coded on a step; includes 'repeats' but not explicitly coded as repeat
## instances of each step code excluding (dual-coded) step repeat + flip
## primary DF for step level analysis
df_steps <- df_steps_raw %>% 
  filter(STEP %nin% c("Step Repeat", "Flipping/Tapping Through Fast")) |> 
  droplevels()


## FOR STEP DURATION GRAPHS
df_steps_dur <- df_steps_raw %>% 
  filter(STEP %nin% c("Step Repeat")) |> 
  droplevels()

## TODO round up ms instead of truncate on timestamps 


## EXPORT DF_STEPS
write.csv(df_steps,"data/output/df_steps.csv", row.names = FALSE)


```

```{r import-errors}

##import errors
## maxQDA export of all retrieved segments for the query (all documents) + (highest level Errors group code [deselect Error Pairs])
## includes error-codes + Error Types + Error Recovery
df_errors_raw <- read_csv("data/input/wip_errors.csv", col_select = 
                       c(`Document name`,
                         `Code`,
                        `Beginning`,
                        `End`
                         ),
                     show_col_types=FALSE) %>% 
    rename(
      START =  `Beginning`,
      END = `End`
    ) %>%
    separate('Document name', into = c("PID", "JAR","FORMAT"), sep = "_") %>% 
    separate('Code', into = c("BLANK","ERROR_GROUP", "ERROR_TYPE","ERROR"), sep = '>') %>% 
    ## strip weird end stuff from times
    separate(END, into = c("END", "JUNK"), sep = ',') %>% 
    separate(START, into = c("START", "JUNK"), sep = ',')  %>% 
  ## FILTER OUT P11 [APP ONLY CONTROL] // P18 [BOOK ONLY CONTROL]
  filter(PID %nin% c("P11", "P18"))%>% 
  mutate(
    PID = as_factor(PID),
    JAR = as_factor(JAR),
    FORMAT = as_factor(FORMAT),
    START = hms::as_hms(START),
    END = hms::as_hms(END),
    DURATION = END-START,
    ERROR_GROUP = as_factor(str_trim(ERROR_GROUP)),
    ERROR_TYPE = as_factor(str_trim(ERROR_TYPE)),
    ERROR = as_factor(str_trim(ERROR))
  ) %>% select(-JUNK, -BLANK)
  
    
## RENAME INSTRUCTION TYPES
df_errors_raw$FORMAT <- fct_recode(df_errors_raw$FORMAT, 
                            "APP" = 'A', 
                            "BOOKLET" = 'B')


## participant level total error count --> sum df_errors w/o error recovery or unresolved 
## participant level unresolved error code --> sum UNRESOLVED UPON COMPLETION 


## DF_ERROR_RECOVERIES
## Error Recovery portion of time when a participant is remediating the error // 
## Unresolved Completion is dual/triple coded with the original error code if they don't recover from it (co-occurs w/ error type)
## only frequency; step codes intersection is not going to be accurate bc it will overlap with wrong step code
df_error_recoveries <- df_errors_raw %>% 
  filter(ERROR_GROUP %in% c("Error Recovery", "Unresolved Upon Completion")) %>% 
  rename(
    "RECOVERY" = "ERROR_GROUP"
  ) %>% 
  select(-ERROR_TYPE, -ERROR)

##DF_ERRORS
##data frame for number of errors; was coded while they were MAKING the error
## more precise durational data about errors should come from the error-pairs extract 
## primary DF for error analysis
df_errors <- df_errors_raw %>% 
  filter(ERROR_GROUP %nin% c("Error Recovery", "Unresolved Upon Completion")) |> 
  select(-ERROR_GROUP)
  # select(-ERROR_TYPE, -ERROR)


## TODO error-step reconcilliation
## TODO EITHER get error-pairs extract from maxqda & parse 
## OR get step code overlap from additional code columns in THIS extract 


## EXPORT DF_ERRORS
write.csv(df_errors,"data/output/df_errors.csv", row.names = FALSE)

```


### TODO participant-level wrangling


## STEPS

### COUNT STEPS 
```{r count-steps}

## SET DATAFRAME
df <- df_steps

print('Number of steps per jar per participant')
table(df$PID, df$JAR)


## GROUPED BARCHART [COUNT STEPS X PARTICIPANT by JAR]
## 
df %>% 
  ggplot(aes(x=PID, fill=JAR))+
    geom_bar(position="dodge") + 
  scale_fill_brewer(palette="Paired", direction =-1) +
  theme_minimal() + 
  labs(title = "Steps per JAR per Participant",
       subtitle = "(includes step repeats)")

## GROUPED BARCHART [COUNT STEPS X PARTICIPANT by FORMAT]
## 
df %>% 
  ggplot(aes(x=PID, fill=FORMAT))+
    geom_bar(position="dodge") + 
      scale_fill_brewer(palette="Set2", direction =-1) +
  theme_minimal() + 
  labs(title = "Steps per FORMAT per Participant",
       subtitle = "(includes step repeats)")



# ## GROUPED BARCHART [COUNT STEPS X PARTICIPANT by JAR facet FORMAT]
g <- df %>%
  ggplot(aes(x=PID, fill=JAR))+
    geom_bar(position="dodge") +
  scale_fill_brewer(palette="Paired", direction =-1) +
  facet_wrap(~FORMAT) +
  theme_minimal() +
  labs(title = "Steps per JAR per Participant BY FORMAT",
       subtitle = "(includes step repeats)")


g
ggsave(
  filename = "figs/step_counts_by_format.svg",
  plot = g,
  device = svglite,
  width = 6,
  height = 4,
  units = "in"
)


```

### DURATION STEPS 

- flipping tapping through fast, should NOT be included in step level duration, but SHOULD be included in participant level duration
```{r duration-steps, warning=FALSE}

## SET DATAFRAME
df <- df_steps

## grouping by participant, jar, format to get duration by step
df_by_step <- df |> 
  group_by(PID,STEP,JAR,FORMAT) |> 
  summarise(
    STEP_DURATION = sum(DURATION)
 )



## DISTRIBUTION OF DURATION BY STEP
g <- df_by_step %>% gf_histogram(~STEP_DURATION, binwidth = 5) +
  facet_grid(JAR~FORMAT) +
  theme_minimal() +
  labs(title = "Distribution of STEP DURATION (in seconds)")

g 
ggsave(
  filename = "figs/step_duration_distribution.svg",
  plot = g,
  device = svglite,
  width = 6,
  height = 4,
  units = "in"
)


## GROUPED BARCHART [SUM STEP DURATION X PARTICIPANT by JAR]
df_steps_dur %>% 
  ggplot(aes(fill=JAR))+
    geom_bar(aes(x=PID, y= DURATION), position="dodge", stat="identity") + 
  scale_fill_brewer(palette="Paired", direction =-1) +
  theme_minimal() + 
  labs(title = "Total step DURATION per JAR per Participant",
       subtitle = "(includes step repeats)")

## GROUPED BARCHART [SUM STEP DURATION X PARTICIPANT by JAR facet FORMAT]
df_steps_dur %>%
    ggplot(aes(fill=FORMAT))+
    scale_fill_brewer(palette="Set2", direction =-1) +
    geom_bar(aes(x=PID, y= DURATION), position="dodge", stat="identity") +
  # facet_wrap(~FORMAT) +
  theme_minimal() +
  labs(title = "Total step DURATION per FORMAT per Participant",
       subtitle = "(includes step repeats)")


```






### DURATION STEPS LINE 
```{r duration-formats}




df <- df_steps%>% 
  group_by(PID, FORMAT,JAR) %>% 
  summarise(
    time = sum(DURATION)
  )

# df %>% gf_histogram(~time) +
#   facet_wrap(~FORMAT) + 
#   theme_minimal()

df %>% ggplot(aes(x=FORMAT, y=time)) +
  geom_jitter(alpha=0.4, width=0.00, aes(color=JAR)) + 
  geom_line(aes(group=PID))+
  theme_minimal() + 
  labs(title = "JAR duration by FORMAT",
       subtitle="line indicates participant")
  


df %>% ggplot(aes(x=FORMAT, y=time)) +
  geom_jitter(alpha=0.4, width=0.00, aes(color=PID)) + 
  geom_line(aes(group=PID))+
  theme_minimal() + 
  labs(title = "JAR duration by FORMAT",
       subtitle="line indicates participant")
  


```





## ERRORS
### COUNT ERRORS 
```{r count-errors}
df <- df_errors

print('Number of errors per jar per participant')
table(df$PID, df$JAR, df$FORMAT)


## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT by JAR]
df %>% 
  ggplot(aes(x=PID, fill=JAR))+
    geom_bar(position="dodge") + 
  theme_minimal() + 
  labs(title = "Errors per JAR per Participant")

## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT by JAR facet FORMAT]
df %>% 
  ggplot(aes(x=PID, fill=JAR))+
    geom_bar(position="dodge") + 
  facet_wrap(~FORMAT) + 
  theme_minimal() + 
  labs(title = "Errors per JAR per Participant BY FORMAT")


## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT by JAR facet FORMAT]
df %>% 
  ggplot(aes(x=PID, fill=FORMAT))+
    geom_bar(position="dodge") + 
  facet_wrap(~ERROR_TYPE) + 
  theme_minimal() + 
  labs(title = "Errors per FORMAT BY TYPE")

## GROUPED BARCHART [COUNT ERRORS X TYPE X FORMAT X ]
df %>% 
  ggplot(aes(x=FORMAT, fill=ERROR_TYPE))+
    geom_bar(position="dodge") + 
  theme_minimal() + 
  labs(title = "Errors by FORMAT and TYPE")

## GROUPED BARCHART [COUNT ERRORS X TYPE X FORMAT X ]
df %>% 
  ggplot(aes(x=FORMAT, fill=ERROR))+
    geom_bar(position="dodge") + 
  theme_minimal() + 
  labs(title = "Errors by FORMAT and ERROR CODE")

## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT facet FORMAT X JAR]
df %>% 
  ggplot(aes(x=PID, fill=ERROR_TYPE))+
    geom_bar() + 
  facet_wrap(JAR~FORMAT) + 
  theme_minimal() + 
  labs(title = "Errors per JAR per Participant BY FORMAT")




```

### COUNT ERROR RECOVERY 
```{r count-recoveries}
df <- df_error_recoveries

print('Number of recovery type per jar per participant')
table(df$PID, df$JAR, df$RECOVERY)


  ## GROUPED BARCHART [COUNT RECOVERIES X by JAR]
df %>% 
  ggplot(aes(x=PID, fill=RECOVERY))+
    geom_bar(position="dodge") + 
  facet_grid(FORMAT~JAR) +
  theme_minimal() + 
  labs(title = "Recoveries per JAR per Participant")

## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT by JAR facet FORMAT]
df %>% 
  ggplot(aes(x=RECOVERY, fill=FORMAT))+
    geom_bar(position="dodge") + 
  # facet_wrap(FORMAT) + 
  theme_minimal() + 
  labs(title = "Errors RECOVERY by FORMAT")
```






## PARTICIPANT LEVEL 



## QUESTIONS 
### STEPS/ERRORS

- Do ppl who have fewer step repeats have more errors?
(visualization of ERRORS X STEP frequency by person)



### STRATEGY

#### organization 

#### strategy X errors
- Will pre-sorting by jar result in less piece selection errors?



- 'flip everything up at start' less piece selection errors?
- does model matching correspond with less (spatial transformation) errors?


### SPEED/ACCURACY 










## STASH

```{r stash}

## REFERENCE CONDITIONAL MUTATE SYNTAX
 # mutate(grade = case_when(
 #    score >= 90 ~ "A",
 #    score >= 80 ~ "B",
 #    TRUE ~ "C"  # Default value
 #  ))



```