---
title: "Lego Assembly Thesis Analysis"
author: "Amy Rae Fox & Zoe Kothari"
date: "2026-05-06"
output:
  html_document:
    theme: cosmo
    code_folding: hide
    fig_caption: yes
    number_sections: no
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    toc_depth: 6
  pdf_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
font-family: DejaVu Sans
mainfont: DejaVu Sans
editor_options: 
  markdown: 
    wrap: 72
---

## SETUP

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) #all the things
library(dplyr) #all the things 
library(lubridate) #timey-wimey
library(ggformula) #regression syntax viz
library(Hmisc) # %nin% operator
library(svglite) #saving ggplots as svgs

## modelling
library(lme4) #regression models
library(lmerTest) #regression models
library(sjPlot) #model plots
library(ggdist) #distributional viz
library(performance) #easyStats compare models
library(report) # ez reporting
library(insight) #ez model info 
library(glmmTMB) #negative binomial glm model 
library(broom.mixed) #tidy model tables mixed effects
```

```{r import-steps}

## DF_STEPS_RAW
## maxQDA export of all retrieved segments for the query (all documents) + (highest level step code [includes each numbered step + Step Repeat + Flipping/Tapping Through Fast])
## NOTE: need to handle Step Repeat + Flipping/Tapping Through Fast seperately 
df_steps_raw <- read_csv("data/input/wip_steps.csv", col_select = 
                       c(`Document name`,
                         `Code`,
                        `Beginning`,
                        `End`
                         ),
                     show_col_types=FALSE) %>% 
    rename(
      START =  `Beginning`,
      END = `End`
    ) %>%
    separate('Document name', into = c("PID", "JAR","FORMAT"), sep = "_") %>% 
    separate('Code', into = c("MASTER_STEP", "STEP"), sep = '>') %>% 
    ## strip weird end stuff from times
    separate(END, into = c("END", "JUNK"), sep = ',') %>% 
    separate(START, into = c("START", "JUNK"), sep = ',') %>% 
  mutate(
    PID = as_factor(PID),
    JAR = as_factor(JAR),
    FORMAT = as_factor(FORMAT),
    # ERROR_GROUP = as_factor(str_trim(ERROR_GROUP)),
    STEP = as_factor(str_trim(STEP)),
    # MASTER_STEP = as_factor(MASTER_STEP),
    START = hms::as_hms(START),
    END = hms::as_hms(END),
    DURATION = END-START
  ) |> 
## FILTER OUT P11 [APP ONLY CONTROL] // P18 [BOOK ONLY CONTROL]
  filter(PID %nin% c("P11", "P18"))%>% 
## REORDER STEP FACTOR LEVELS
  mutate(
    STEP = fct_relevel(STEP, "Step 0A","Step 0B")
  ) |> 
  select(-JUNK, -MASTER_STEP) |> 
  droplevels()


## RENAME INSTRUCTION TYPES
df_steps_raw$FORMAT <- fct_recode(df_steps_raw$FORMAT, 
                            "APP" = 'A', 
                            "BOOKLET" = 'B')

## DF_STEP_REPEATS
## The Step Repeat is a dual code (alongside the numbered step), applied whenever a participant meaninfully repeated the actions of a step while looking at the instructions for the step (e.g. potentially during an error recovery) 
## NOT included in PARTICIPANT count of steps (dual code would add doubles) 
## NOT included in PARTICIPANT step-level duration (dual code would add doubles)
df_step_repeats <- df_steps_raw |> 
  filter( STEP == "Step Repeat")


## DF_STEP_FLIPPING
## The 'Flipping/Tapping Through Fast code indicates when participant is engaging with instructions in order to navigate to a different point rather than meaningfully with THAT step
## TODO flipping/tapping SHOULD be included in Participant level total step duration 
## TODO flipping/tapping SHOULD NOT be included in Participant level step count 
df_step_flipping <- df_steps_raw |> 
  filter( STEP == "Flipping/Tapping Through Fast")


##DF_STEPS
##data frame for time coded on a step; includes 'repeats' but not explicitly coded as repeat
## instances of each step code excluding (dual-coded) step repeat + flip
## primary DF for step level analysis
df_steps <- df_steps_raw %>% 
  filter(STEP %nin% c("Step Repeat", "Flipping/Tapping Through Fast")) |> 
  droplevels()


## FOR STEP DURATION GRAPHS
df_steps_dur <- df_steps_raw %>% 
  filter(STEP %nin% c("Step Repeat")) |> 
  droplevels()

## TODO round up ms instead of truncate on timestamps 


## EXPORT DF_STEPS
write.csv(df_steps,"data/output/df_steps.csv", row.names = FALSE)


```

```{r import-errors}

##import errors
## maxQDA export of all retrieved segments for the query (all documents) + (highest level Errors group code [deselect Error Pairs])
## includes error-codes + Error Types + Error Recovery
df_errors_raw <- read_csv("data/input/wip_errors.csv", col_select = 
                       c(`Document name`,
                         `Code`,
                        `Beginning`,
                        `End`
                         ),
                     show_col_types=FALSE) %>% 
    rename(
      START =  `Beginning`,
      END = `End`
    ) %>%
    separate('Document name', into = c("PID", "JAR","FORMAT"), sep = "_") %>% 
    separate('Code', into = c("BLANK","ERROR_GROUP", "ERROR_TYPE","ERROR"), sep = '>') %>% 
    ## strip weird end stuff from times
    separate(END, into = c("END", "JUNK"), sep = ',') %>% 
    separate(START, into = c("START", "JUNK"), sep = ',')  %>% 
  ## FILTER OUT P11 [APP ONLY CONTROL] // P18 [BOOK ONLY CONTROL]
  filter(PID %nin% c("P11", "P18"))%>% 
  mutate(
    PID = as_factor(PID),
    JAR = as_factor(JAR),
    FORMAT = as_factor(FORMAT),
    START = hms::as_hms(START),
    END = hms::as_hms(END),
    DURATION = END-START,
    ERROR_GROUP = as_factor(str_trim(ERROR_GROUP)),
    ERROR_TYPE = as_factor(str_trim(ERROR_TYPE)),
    ERROR = as_factor(str_trim(ERROR))
  ) %>% select(-JUNK, -BLANK)
  
    
## RENAME INSTRUCTION TYPES
df_errors_raw$FORMAT <- fct_recode(df_errors_raw$FORMAT, 
                            "APP" = 'A', 
                            "BOOKLET" = 'B')


## participant level total error count --> sum df_errors w/o error recovery or unresolved 
## participant level unresolved error code --> sum UNRESOLVED UPON COMPLETION 


## DF_ERROR_RECOVERIES
## Error Recovery portion of time when a participant is remediating the error // 
## Unresolved Completion is dual/triple coded with the original error code if they don't recover from it (co-occurs w/ error type)
## only frequency; step codes intersection is not going to be accurate bc it will overlap with wrong step code
df_error_recoveries <- df_errors_raw %>% 
  filter(ERROR_GROUP %in% c("Error Recovery", "Unresolved Upon Completion")) %>% 
  rename(
    "RECOVERY" = "ERROR_GROUP"
  ) %>% 
  select(-ERROR_TYPE, -ERROR)

##DF_ERRORS
##data frame for number of errors; was coded while they were MAKING the error
## more precise durational data about errors should come from the error-pairs extract 
## primary DF for error analysis
df_errors <- df_errors_raw %>% 
  filter(ERROR_GROUP %nin% c("Error Recovery", "Unresolved Upon Completion")) |> 
  select(-ERROR_GROUP)
  # select(-ERROR_TYPE, -ERROR)


## TODO error-step reconcilliation
## TODO EITHER get error-pairs extract from maxqda & parse 
## OR get step code overlap from additional code columns in THIS extract 


## EXPORT DF_ERRORS
write.csv(df_errors,"data/output/df_errors.csv", row.names = FALSE)

```

```{r import-participants}

##import participants
## manually generated participant level file based on covariate data + participant survey
df_participants_raw <- read_csv("data/input/participants.csv", 
                     show_col_types=FALSE) |> 
  mutate(
    PID = as_factor(PID),
    Gender = as_factor(Gender),
    Experience_LEGO = as_factor(Experience_LEGO),
    Experience_DIY = as_factor(Experience_DIY),
    Childhood_LEGO = as_factor(Childhood_LEGO)
    # END = hms::as_hms(END),
  ) |> 
  ## FILTER OUT P11 [APP ONLY CONTROL] // P18 [BOOK ONLY CONTROL]
  filter(PID %nin% c("P11", "P18")) |> 
  droplevels()
  
## corsi backward span score == length of the longest sequence of colored blocks for which the participant successfully recalled at least one of the trials 


## EXPORT DF_ERRORS
# write.csv(df_errors,"data/output/df_errors.csv", row.names = FALSE)

```

### TODO participant-level wrangling
### TODO import error pairs
### TODO import step-pair 

## TODO ERROR PAIR 
### ERROR COUNT per STEP
### ERROR TYPE per STEP

## STEPS

### COUNT STEPS

```{r count-steps}

## SET DATAFRAME
df <- df_steps

print('Number of steps per jar per participant')
table(df$PID, df$JAR)


## GROUPED BARCHART [COUNT STEPS X PARTICIPANT by JAR]
## 
df %>% 
  ggplot(aes(x=PID, fill=JAR))+
    geom_bar(position="dodge") + 
  scale_fill_brewer(palette="Paired", direction =-1) +
  theme_minimal() + 
  labs(title = "Steps per JAR per Participant",
       subtitle = "(includes step repeats)")

## GROUPED BARCHART [COUNT STEPS X PARTICIPANT by FORMAT]
## 
df %>% 
  ggplot(aes(x=PID, fill=FORMAT))+
    geom_bar(position="dodge") + 
      scale_fill_brewer(palette="Set2", direction =-1) +
  theme_minimal() + 
  labs(title = "Steps per FORMAT per Participant",
       subtitle = "(includes step repeats)")



# ## GROUPED BARCHART [COUNT STEPS X PARTICIPANT by JAR facet FORMAT]
g <- df %>%
  ggplot(aes(x=PID, fill=JAR))+
    geom_bar(position="dodge") +
  scale_fill_brewer(palette="Paired", direction =-1) +
  facet_wrap(~FORMAT) +
  theme_minimal() +
  labs(title = "Steps per JAR per Participant BY FORMAT",
       subtitle = "(includes step repeats)")


g
ggsave(
  filename = "figs/step_counts_by_format.svg",
  plot = g,
  device = svglite,
  width = 6,
  height = 4,
  units = "in"
)


```

### DURATION STEPS

#### STEP-LEVEL DURATION (BAR)
-   flipping tapping through fast, should NOT be included in step level
    duration, but SHOULD be included in participant level duration

```{r duration-steps, warning=FALSE}

## SET DATAFRAME
df <- df_steps

## grouping by participant, jar, format to get duration by step
df_by_step <- df |> 
  group_by(PID,STEP,JAR,FORMAT) |> 
  summarise(
    STEP_DURATION = sum(DURATION)
 )



## DISTRIBUTION OF DURATION BY STEP
g <- df_by_step %>% gf_histogram(~STEP_DURATION, binwidth = 5) +
  facet_grid(JAR~FORMAT) +
  theme_minimal() +
  labs(title = "Distribution of STEP DURATION (in seconds)")

g 
ggsave(
  filename = "figs/step_duration_distribution.svg",
  plot = g,
  device = svglite,
  width = 6,
  height = 4,
  units = "in"
)


## GROUPED BARCHART [SUM STEP DURATION X PARTICIPANT by JAR]
df_steps_dur %>% 
  ggplot(aes(fill=JAR))+
    geom_bar(aes(x=PID, y= DURATION), position="dodge", stat="identity") + 
  scale_fill_brewer(palette="Paired", direction =-1) +
  theme_minimal() + 
  labs(title = "Total step DURATION per JAR per Participant",
       subtitle = "(includes step repeats)")

## GROUPED BARCHART [SUM STEP DURATION X PARTICIPANT by JAR facet FORMAT]
df_steps_dur %>%
    ggplot(aes(fill=FORMAT))+
    scale_fill_brewer(palette="Set2", direction =-1) +
    geom_bar(aes(x=PID, y= DURATION), position="dodge", stat="identity") +
  # facet_wrap(~FORMAT) +
  theme_minimal() +
  labs(title = "Total step DURATION per FORMAT per Participant",
       subtitle = "(includes step repeats)")


```

#### JAR-LEVEL DURATION (LINE)

```{r duration-formats}

df <- df_steps%>% 
  group_by(PID, FORMAT,JAR) %>% 
  summarise(
    time = sum(DURATION)
  )

# df %>% gf_histogram(~time) +
#   facet_wrap(~FORMAT) + 
#   theme_minimal()

df %>% ggplot(aes(x=FORMAT, y=time)) +
  geom_jitter(alpha=0.4, width=0.00, aes(color=JAR)) + 
  geom_line(aes(group=PID))+
  theme_minimal() + 
  labs(title = "JAR duration by FORMAT",
       subtitle="line indicates participant")
  

## PId level connected line plot 
g <- df %>% ggplot(aes(x=FORMAT, y=time)) +
  geom_jitter(alpha=0.4, width=0.00, aes(color=PID)) + 
  geom_line(aes(group=PID))+
  theme_minimal() + 
  labs(title = "JAR duration by FORMAT",
       subtitle="line indicates participant")
  
g 
ggsave(
  filename = "figs/jar_duration_by_participant_line.svg",
  plot = g,
  device = svglite,
  width = 6,
  height = 4,
  units = "in"
)



```
#### JAR-LEVEL DURATION (BAR)

```{r duration-steps-participant, warning=FALSE}

## SET DATAFRAME


## grouping by participant, jar, format to get duration by step
df <- df_duration_by_particiapnt <- df_steps |> 
  group_by(PID,JAR,FORMAT) |> 
  summarise(
    DURATION = sum(DURATION)
 )


## GROUPED BARCHART [all participants total DURATION X PARTICIPANT by JAR facet FORMAT]
df %>%
    ggplot(aes(fill=JAR))+
    scale_fill_brewer(palette="Paired", direction =-1) +
    geom_bar(aes(x=FORMAT, y= DURATION), position="dodge", stat="identity") +
  # facet_wrap(~FORMAT) +
  theme_minimal() +
  labs(title = "Total step DURATION per FORMAT per Participant",
       subtitle = "(includes step repeats)")


```
#### JAR-LEVEL DURATION (GGSTATSPLOT)

```{r duration-participant, warning=FALSE}

## SET DATAFRAME


## grouping by participant, jar, format to get duration by step
df <- df_duration_by_particiapnt <- df_steps |> 
  group_by(PID,JAR, FORMAT) |> 
  summarise(
    DURATION = as.double(sum(DURATION))
 )


library(ggstatsplot)
grouped_ggwithinstats(df, x=FORMAT, y=DURATION, 
                      grouping.var = JAR, 
                      subject.id = PID,
                      type = "parametric",
    pairwise.comparisons = TRUE)

```


## ERRORS

### COUNT ERRORS

```{r count-errors}
df <- df_errors

print('Number of errors per jar per participant')
table(df$PID, df$JAR, df$FORMAT)


## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT by JAR]
df %>% 
  ggplot(aes(x=PID, fill=JAR))+
    geom_bar(position="dodge") + 
  scale_fill_brewer(palette="Paired", direction =-1) +
  theme_minimal() + 
  labs(title = "Errors per JAR per Participant")

## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT by JAR facet FORMAT]
df %>% 
  ggplot(aes(x=PID, fill=JAR))+
  scale_fill_brewer(palette="Paired", direction =-1) +
    geom_bar(position="dodge") + 
  facet_wrap(~FORMAT) + 
  theme_minimal() + 
  labs(title = "Errors per JAR per Participant BY FORMAT")


## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT by JAR facet FORMAT]
df %>% 
  ggplot(aes(x=PID, fill=FORMAT))+
    geom_bar(position="dodge") + 
  facet_wrap(~ERROR_TYPE) + 
  theme_minimal() + 
  labs(title = "Errors per FORMAT BY TYPE")

## GROUPED BARCHART [COUNT ERRORS X TYPE X FORMAT X ]
df %>% 
  ggplot(aes(x=FORMAT, fill=ERROR_TYPE))+
    geom_bar(position="dodge") + 
  theme_minimal() + 
  labs(title = "Errors by FORMAT and TYPE")

## FACETED GROUPED BARCHART [COUNT ERRORS X TYPE X FORMAT X ]
df %>% 
  ggplot(aes(x=FORMAT, fill=ERROR_TYPE))+
    geom_bar(position="dodge") + 
  facet_wrap(~JAR) + 
  theme_minimal() + 
  labs(title = "Errors by FORMAT and TYPE")


## GROUPED BARCHART [COUNT ERRORS X TYPE X FORMAT X ]
df %>% 
  ggplot(aes(x=FORMAT, fill=ERROR))+
    geom_bar(position="dodge") + 
  theme_minimal() + 
  labs(title = "Errors by FORMAT and ERROR CODE")

## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT facet FORMAT X JAR]
df %>% 
  ggplot(aes(x=PID, fill=ERROR_TYPE))+
    geom_bar() + 
  facet_wrap(JAR~FORMAT) + 
  theme_minimal() + 
  labs(title = "Errors per JAR per Participant BY FORMAT")





## ZOES DETAIL GRAPH
g <- df %>% 
  ggplot(aes(x=ERROR_TYPE, fill=ERROR))+
    geom_bar(stat="count") + 
  facet_wrap(~FORMAT) +
  theme_minimal() + 
  labs(title = "Errors by FORMAT and TYPE")

g 
ggsave(
  filename = "figs/errors_by_format_type.svg",
  plot = g,
  device = svglite,
  width = 10,
  height = 4,
  units = "in"
)



```

### COUNT ERROR RECOVERY

```{r count-recoveries}
df <- df_error_recoveries

print('Number of recovery type per jar per participant')
table(df$PID, df$JAR, df$RECOVERY)


  ## GROUPED BARCHART [COUNT RECOVERIES X by JAR]
df %>% 
  ggplot(aes(x=PID, fill=RECOVERY))+
    geom_bar(position="dodge") + 
  facet_grid(FORMAT~JAR) +
  theme_minimal() + 
  labs(title = "Recoveries per JAR per Participant")

## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT by FORMAT]
df %>% 
  ggplot(aes(x=RECOVERY, fill=FORMAT))+
    geom_bar(position="dodge") + 
  # facet_wrap(FORMAT) + 
  theme_minimal() + 
  labs(title = "Errors RECOVERY by FORMAT")

## GROUPED BARCHART [COUNT ERRORS X PARTICIPANT by FORMAT and JAR]
df %>% 
  ggplot(aes(x=RECOVERY, fill=FORMAT))+
    geom_bar(position="dodge") + 
  facet_wrap(~JAR) + 
  theme_minimal() + 
  labs(title = "Errors RECOVERY by FORMAT and JAR")


## GROUPED BARCHART []
df %>% 
  ggplot(aes(x=FORMAT, fill=RECOVERY))+
    geom_bar() + 
  scale_fill_brewer(palette="Paired", direction =1) +
  facet_wrap(~JAR) + 
  theme_minimal() + 
  labs(title = "Errors RECOVERY by FORMAT")


## GROUPED BARCHART []
g <- df %>% 
  ggplot(aes(x=FORMAT, fill=RECOVERY))+
    geom_bar() + 
  scale_fill_brewer(palette="Paired", direction =1) +
  facet_wrap(~JAR) + 
  theme_minimal() + 
  labs(title = "Errors RECOVERY by FORMAT")

g 
ggsave(
  filename = "figs/errors_recovery.svg",
  plot = g,
  device = svglite,
  width = 6,
  height = 4,
  units = "in"
)

```
#### todo 
- ratio of recovered to unrecovered 



## OPEN QUESTIONS

### ZOES FOUR THINGS
#### complexity score
#### by participant experience
#### by corsi 
#### participant strategy 
mean step 0 time 
step 0 team 
#### time——accuracy -- import error pairs 
#### step pairs 



### STEPS/ERRORS

-   Do ppl who have fewer step repeats have more errors? (visualization
    of ERRORS X STEP frequency by person)

### STRATEGY

#### organization

#### strategy X errors

-   Will pre-sorting by jar result in less piece selection errors?

-   'flip everything up at start' less piece selection errors?

-   does model matching correspond with less (spatial transformation)
    errors?

### SPEED/ACCURACY





## MODELS

### PARTICIPANT LEVEL DURATION MODEL

### Step Duration

What predicts duration per step?

- TODO add fixed effect of experience
- TODO explore fixed effect of step number

```{r time-vis}

## predict step time by format and participant
df <- df_steps_dur %>% 
  mutate(
    dur = as.double(DURATION)
  )

## PLOT RAW DATA   
## STRIP PLOT + MEAN LABEL
ggplot(df, aes(x = FORMAT, y = dur, colour = FORMAT)) +
  geom_boxplot(
    aes(group = FORMAT),
    width = 0.5,
    outlier.shape = NA
  ) +
  geom_jitter(
    width = 0.1,
    alpha = 0.6,
    size = 0.5
  ) +
  # DISPLAY MEAN AS POINT
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 18,
    size = 3,
    colour = "black"
  ) +
  # MEAN LABEL
  stat_summary(
    fun = mean,
    geom = "text",
    aes(label = paste("M=",sprintf("%.2f", after_stat(y)))),
    vjust = -0.8,
    colour = "black",
    size = 3
  ) +
  facet_wrap(~ JAR) +
  theme_minimal() + 
  labs(title = "Step Duration by Format & Jar",
       y = "Duration (s)")



# ######## DROP OUTLINES 
# ### DROP P10, P13
# df <- df |> filter(PID %nin% c("P10", "P13")) |> droplevels()
# 
# 
# ## PLOT RAW DATA   
# ## STRIP PLOT + MEAN LABEL
# ggplot(df, aes(x = FORMAT, y = dur, colour = FORMAT)) +
#   geom_boxplot(
#     aes(group = FORMAT),
#     width = 0.5,
#     outlier.shape = NA
#   ) +
#   geom_jitter(
#     width = 0.1,
#     alpha = 0.6,
#     size = 0.5
#   ) +
#   # DISPLAY MEAN AS POINT
#   stat_summary(
#     fun = mean,
#     geom = "point",
#     shape = 18,
#     size = 3,
#     colour = "black"
#   ) +
#   # MEAN LABEL
#   stat_summary(
#     fun = mean,
#     geom = "text",
#     aes(label = paste("M=",sprintf("%.2f", after_stat(y)))),
#     vjust = -0.8,
#     colour = "black",
#     size = 3
#   ) +
#   facet_wrap(~ JAR) +
#   theme_minimal() + 
#   labs(title = "Step Duration by Format & Jar",
#        y = "Duration (s)")



```

```{r model-time}

## predict step time by format and participant
df <- df_steps_dur %>% 
  mutate(
    dur = as.double(DURATION)
  )

## MODEL 1 | Simple Main Effects
m1 <- lmer(dur ~ FORMAT + JAR + (1|PID), data = df)
summary(m1)
anova(m1)
report(m1)

## MODEL 2 | Interaction Main Effects
# m2 <- lmer(dur ~ FORMAT * JAR + (1|PID), data = df)
# summary(m2)
# anova(m2)
# compare_performance(m1,m2, rank = TRUE)
## interaction model is not a better fit

## PLOT MODEL ESTIMATES
# plot_model(m1, show.values= TRUE, type = "re") # random effects
 plot_model(m1, show.values= TRUE, type = "est", title = "Model Estimate (dur ~ FORMAT + JAR + (1|PID)")

## DESCRIBE MODEL VARIANCE EXPLAINED
v <- get_variance(m1)
t <- v$var.fixed + v$var.random + v$var.residual
fixed <- v$var.fixed/t * 100
random <- v$var.random/t * 100
residual <- v$var.residual/t * 100

## MODEL TABLE
m1_tab <- tidy(m1, effects = "fixed") %>%
  mutate(
    estimate  = round(estimate, 2),
    std.error = round(std.error, 2),
    statistic = round(statistic, 2),
    p.value   = ifelse(
      p.value < .001,
      "< .001",
      sprintf("= %.3f", p.value)
    )
  )
format_row <- filter(m1_tab, term == "FORMATAPP")
jar_row    <- filter(m1_tab, term == "JARjar2")
int_row    <- filter(m1_tab, term == "(Intercept)")

```

A linear mixed-effects model was fit to predict step duration from
FORMAT and JAR, with a random intercept for participant (PID).

The effect of FORMAT was not statistically significant, β =
`r format_row$estimate`, SE = `r format_row$std.error`, *t* =
`r format_row$statistic`, *p* `r format_row$p.value`.

In contrast, JAR significantly predicted step duration, β =
`r jar_row$estimate`, SE = `r jar_row$std.error`, *t* =
`r jar_row$statistic`, *p* `r jar_row$p.value`, indicating that steps
performed in Jar 2 took approximately `r jar_row$estimate` seconds
longer than those performed in Jar 1.

The estimated mean duration in the reference condition was
`r int_row$estimate` seconds (SE = `r int_row$std.error`).

The participant-level variance was `r round(v$var.random, 2)` and the
residual variance was `r round(v$var.residual, 2)`.

*Fixed effects accounted for approximately
`r round(100 * v$var.fixed / (v$var.fixed + v$var.random + v$var.residual), 1)`%
of the total variance, participant-level differences accounted for
`r round(100 * v$var.random / (v$var.fixed + v$var.random + v$var.residual), 1)`%,
and
`r round(100 * v$var.residual / (v$var.fixed + v$var.random + v$var.residual), 1)`%
remained unexplained.*

### Error Count
What predicts number of errors?


```{r setup-error-counts}

## generate error counts df
error_counts_obs <- df_errors %>%
  count(PID, JAR, FORMAT, name = "n_errors")

assignments <- error_counts_obs %>%
  group_by(PID) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(
    sequence = case_when(
      (JAR == "jar1" & FORMAT == "APP") |
      (JAR == "jar2" & FORMAT == "BOOKLET") ~ "A",

      (JAR == "jar1" & FORMAT == "BOOKLET") |
      (JAR == "jar2" & FORMAT == "APP") ~ "B"
    )
  )

valid_conditions <- assignments %>%
  select(PID, sequence) %>%
  uncount(2) %>%
  group_by(PID, sequence) %>%
  mutate(
    JAR = if_else(row_number() == 1, "jar1", "jar2"),
    FORMAT = case_when(
      sequence == "A" & JAR == "jar1" ~ "APP",
      sequence == "A" & JAR == "jar2" ~ "BOOKLET",
      sequence == "B" & JAR == "jar1" ~ "BOOKLET",
      sequence == "B" & JAR == "jar2" ~ "APP"
    )
  ) %>%
  ungroup() %>%
  select(PID, JAR, FORMAT)

error_counts <- valid_conditions %>%
  left_join(
    error_counts_obs,
    by = c("PID", "JAR", "FORMAT")
  ) %>%
  mutate(
    n_errors = replace_na(n_errors, 0)
  ) %>%
  arrange(PID, JAR)

rm(error_counts_obs, valid_conditions)
```

```{r error-vis}

## set dataframe
df <- error_counts

ggplot(error_counts,
       aes(x = FORMAT,
           y = n_errors,
           colour = JAR)) +
  geom_boxplot(
    aes(group = FORMAT),
    outlier.shape = NA
  ) +
  geom_jitter(width = 0.08, alpha = 0.6) +
    # DISPLAY MEAN AS POINT
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 18,
    size = 3,
    colour = "black"
  ) +
  # MEAN LABEL
  stat_summary(
    fun = mean,
    geom = "text",
    aes(label = paste("M=",sprintf("%.2f", after_stat(y)))),
    vjust = -0.8,
    colour = "black",
    size = 3
  ) +
  facet_wrap(~ JAR) +
  theme_minimal() + 
  labs(title = "Error Count by Format & Jar", 
       y = "Number of Errors")


## INDIVIDUAL DIFFERENCES BY JAR
ggplot(df, aes(x = JAR, y = n_errors, group = PID)) +
  geom_line(alpha = 0.35) +
  geom_point(size = 2, alpha = 0.8) +
  theme_bw() +
  labs(
    x = "Jar",
    y = "Error Count"
  )+ 
  theme_minimal() + 
  labs(title = "Error Count by JAR",
                         subtitle = "(lines connect PIDs)")

## INDIVIDUAL DIFFERENCES BY JAR
ggplot(df, aes(x = FORMAT, y = n_errors, group = PID)) +
  geom_line(alpha = 0.35) +
  geom_point(size = 2, alpha = 0.8) +
  theme_bw() +
  labs(
    x = "Format",
    y = "Error Count"
  )+
  theme_minimal() + 
  labs(title = "Error Count by FORMAT",
                         subtitle = "(lines connect PIDs)")



######## DROP OUTLINES 
### DROP P10, P13
df <- df |> filter(PID %nin% c("P10", "P13")) |> droplevels()


### removed 
ggplot(df,
       aes(x = FORMAT,
           y = n_errors,
           colour = JAR)) +
  geom_boxplot(
    aes(group = FORMAT),
    outlier.shape = NA
  ) +
  geom_jitter(width = 0.08, alpha = 0.6) +
    # DISPLAY MEAN AS POINT
  stat_summary(
    fun = mean,
    geom = "point",
    shape = 18,
    size = 3,
    colour = "black"
  ) +
  # MEAN LABEL
  stat_summary(
    fun = mean,
    geom = "text",
    aes(label = paste("M=",sprintf("%.2f", after_stat(y)))),
    vjust = -0.8,
    colour = "black",
    size = 3
  ) +
  facet_wrap(~ JAR) +
  theme_minimal() + 
  labs(title = "Error Count by Format & Jar", 
       y = "Number of Errors")


## INDIVIDUAL DIFFERENCES BY JAR
ggplot(df, aes(x = JAR, y = n_errors, group = PID)) +
  geom_line(alpha = 0.35) +
  geom_point(size = 2, alpha = 0.8) +
  theme_bw() +
  labs(
    x = "Jar",
    y = "Error Count"
  )+ 
  theme_minimal() + 
  labs(title = "Error Count by JAR",
                         subtitle = "(lines connect PIDs)")

## INDIVIDUAL DIFFERENCES BY JAR
ggplot(df, aes(x = FORMAT, y = n_errors, group = PID)) +
  geom_line(alpha = 0.35) +
  geom_point(size = 2, alpha = 0.8) +
  theme_bw() +
  labs(
    x = "Format",
    y = "Error Count"
  )+
  theme_minimal() + 
  labs(title = "Error Count by FORMAT",
                         subtitle = "(lines connect PIDs)")


```



```{r model-error-poisson}

## df = error counts dataframe
df <- error_counts 

######## DROP OUTLINES 
### DROP P10, P13
df <- df |> filter(PID %nin% c("P10", "P13")) |> droplevels()

## MODEL 1 | Poisson model for count data
m_pois <- glmer(
  n_errors ~ FORMAT + JAR + (1|PID),
  family = poisson,
  data = df
)
summary(m_pois)
check_overdispersion(m_pois)
# anova(m_pois)
# report(m_pois)







## PLOT MODEL ESTIMATES
# plot_model(m_pois, show.values= TRUE, type = "re") # random effects
plot_model(m_pois, show.values= TRUE, type = "est", title = "Model Estimate (n_errors ~ FORMAT + JAR + (1|PID), family = poisson")


## MODEL TABLE
m_pois_tab <- tidy(m_pois, effects = "fixed") %>%
  mutate(
    beta = round(estimate, 2),
    se   = round(std.error, 2),
    z    = round(statistic, 2),
    p    = ifelse(p.value < .001, "< .001", paste0("= ", round(p.value, 3))),
    irr  = round(exp(estimate), 2),
    pct_change = round((exp(estimate) - 1) * 100, 0)
  )

format_booklet <- m_pois_tab %>% filter(term == "FORMATBOOKLET")
jar2           <- m_pois_tab %>% filter(term == "JARjar2")
intercept      <- m_pois_tab %>% filter(term == "(Intercept)")

## RANDOM EFFECT
re_var <- as.data.frame(VarCorr(m_pois)) %>%
  filter(grp == "PID") %>%
  pull(vcov)

re_sd <- as.data.frame(VarCorr(m_pois)) %>%
  filter(grp == "PID") %>%
  pull(sdcor)

## OVERDISPERSION
od <- performance::check_overdispersion(m_pois)

## DESCRIBE MODEL VARIANCE EXPLAINED
v_pois <- get_variance(m_pois,   tolerance = 1e-12)
total_var <- v_pois$var.fixed +
             v_pois$var.random +
             v_pois$var.residual

fixed_pct <- 100 * v_pois$var.fixed / total_var
random_pct <- 100 * v_pois$var.random / total_var
resid_pct <- 100 * v_pois$var.residual / total_var

```

A Poisson generalized linear mixed-effects model was fit to predict error count from FORMAT and JAR, with a random intercept for participant (PID). A significant effect of JAR was observed, with Jar 2 associated with higher error counts than Jar 1 (β = `r jar2$beta`, SE = `r jar2$se`, *z* = `r jar2$z`, *p* `r jar2$p`). Exponentiating the coefficient indicated that expected error counts were approximately `r jar2$pct_change`% higher in Jar 2 than in Jar 1 (IRR = `r jar2$irr`). The effect of FORMAT was not statistically significant (β = `r format_booklet$beta`, SE = `r format_booklet$se`, *z* = `r format_booklet$z`, *p* `r format_booklet$p`), although error counts were estimated to be approximately `r format_booklet$pct_change`% higher for BOOKLET than APP (IRR = `r format_booklet$irr`). The participant-level random intercept variance was `r round(re_var, 2)` (SD = `r round(re_sd, 2)`). 

Variance decomposition indicated that fixed effects accounted for approximately `r round(fixed_pct, 1)`% of the total variance, participant-level variability accounted for `r round(random_pct, 1)`%, and `r round(resid_pct, 1)`% remained unexplained. 

An overdispersion diagnostic found no evidence that the Poisson assumption was violated (dispersion ratio = `r round(od$dispersion_ratio, 2)`, *p* = `r ifelse(od$p_value < .001, "< .001", paste0("= ", round(od$p_value, 3)))`).

```{r model-error-negativeBIONOM}
# ## MODEL 2 | Negative binomial model for overdispersed count data
# m_nb <- glmmTMB(
#   n_errors ~ FORMAT + JAR + (1|PID),
#   family = nbinom2, 
#   data = error_counts
# )
# summary (m_nb)
# report(m_nb)
# 
# ## PLOT MODEL ESTIMATES
# plot_model(m_nb, values = TRUE, type = "est",
#            title = "Model Prediction for (n_errors n_errors ~ FORMAT + JAR + (1|PID) [family = nbinom2]")
# 
# 
# ## MODEL TABLE
# m_nb_tab <- tidy(m_nb, effects = "fixed") %>%
#   mutate(
#     beta = round(estimate, 2),
#     se   = round(std.error, 2),
#     z    = round(statistic, 2),
#     p    = ifelse(p.value < .001, "< .001", paste0("= ", round(p.value, 3)))
#   )
# 
# #m_nb_tab
# format_app <- m_nb_tab %>% filter(term == "FORMATAPP")
# jar2       <- m_nb_tab %>% filter(term == "JARjar2")
# re_var <- as.data.frame(VarCorr(m_nb)$cond$PID)[1, 1]
# 
# ## DESCRIBE MODEL VARIANCE EXPLAINED
# v_nb <- get_variance(m_nb,   tolerance = 1e-12)
# total_var <- v_nb$var.fixed +
#              v_nb$var.random +
#              v_nb$var.residual
# 
# fixed_pct <- 100 * v_nb$var.fixed / total_var
# random_pct <- 100 * v_nb$var.random / total_var
# resid_pct <- 100 * v_nb$var.residual / total_var


# A negative binomial generalized linear mixed-effects model was fit to
# predict error counts from FORMAT and JAR, with a random intercept for
# participant (PID). Neither predictor was significantly associated with
# error count. Relative to the reference format, the APP format was
# associated with a non-significant reduction in expected errors (β =
# `r format_app$beta`, SE = `r format_app$se`, z = `r format_app$z`, p
# `r format_app$p`). Similarly, Jar 2 was associated with a
# non-significant increase in expected errors relative to Jar 1 (β =
# `r jar2$beta`, SE = `r jar2$se`, z = `r jar2$z`, p `r jar2$p`). The
# participant-level random-intercept variance was `r signif(re_var, 3)`,
# indicating little evidence of systematic between-participant differences
# in baseline error rates.
# 
# Variance decomposition indicated that fixed effects accounted for approximately `r round(fixed_pct,2)`% of the total variance, participant-level variability accounted for `r  format(random_pct, scientific=FALSE)`%, and `r round(resid_pct,2)`% remained unexplained.
```



### TODO Predict Error TYPE by FORMAT

```{r }

df <- df_errors

## PREDICT TYPE by FORMAT 

library(glmmTMB)

m1 <- glmmTMB(
  ERROR_TYPE ~ FORMAT + JAR + (1 | PID),
  data = df,
  family = multinomial()
)


library(brms)

model <- brm(
  ERROR_TYPE ~ FORMAT + JAR + (1 | PID),
  data = df,
  family = categorical()
)



install.packages("mclogit")
library(mclogit)

model <- mblogit(
  ERROR_TYPE ~ FORMAT + JAR,
  random = ~ 1 | PID,
  data = df
)


```
### TODO Predict Error TYPE by STEP X FORMAT 





## PREDICT RECOVERY 

### vis

```{r}

df <- df_error_recoveries




## GROUPED BARCHART []
df %>% 
  ggplot(aes(x=FORMAT, fill=RECOVERY))+
    geom_bar() + 
  scale_fill_brewer(palette="Paired", direction =1) +
  facet_wrap(~JAR) + 
  theme_minimal() + 
  labs(title = "Errors RECOVERY by FORMAT")


## GROUPED BARCHART []
df %>% 
  ggplot(aes(x=FORMAT, fill=RECOVERY))+
    geom_bar() + 
  scale_fill_brewer(palette="Paired", direction =1) +
  facet_wrap(~JAR) + 
  theme_minimal() + 
  labs(title = "Errors RECOVERY by FORMAT")


```


### model 
```{r errors-recovery}

## one row per error
df <- df_error_recoveries |> 
  droplevels() |> 
   mutate(RECOVERY = fct_rev(RECOVERY))

m1 <- glmer(
  RECOVERY ~ FORMAT + JAR + (1 | PID),
  data = df,
  family = binomial(link = "logit")
)

m2 <- glmer(
  RECOVERY ~ FORMAT * JAR + (1 | PID),
  data = df,
  family = binomial(link = "logit")
)





```


## STASH

```{r stash}

## REFERENCE CONDITIONAL MUTATE SYNTAX
 # mutate(grade = case_when(
 #    score >= 90 ~ "A",
 #    score >= 80 ~ "B",
 #    TRUE ~ "C"  # Default value
 #  ))



```
